### 2018-03-11 article/article_1.tex
ordenando

\documentclass[review]{elsarticle}
\usepackage{comment}
\usepackage{url}
%
\usepackage[breaklinks]{hyperref}
\usepackage{breakurl}

\usepackage[ruled]{algorithm2e}

%\usepackage{lineno}
%\modulolinenumbers[5]

\journal{Optics Communications}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{subcaption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Illumination Level Independence in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{-------- ------- ------}
\author{-------- ------- ------}

% \author{Fernando Pujaico Rivera\fnref{myfootnote2}}
% \author{Roberto Alves Braga Jr.\fnref{myfootnote1}}
% \address{University Federal of Lavras, Lavras, Brazil}
% \fntext[myfootnote2]{201518201@posgrad.ufla.br}
% \fntext[myfootnote1]{robertobraga@deg.ufla.br }

\begin{abstract}
In this article we show an analysis of how the frequency band,
of the speckle signal, influence in the
light independence of the speckle index value in a dynamic laser speckle analysis. 
Specifically, 
will be studied as It is influenced the temporal speckle deviation 
index by the use of 3 different frequency bands of the speckle signal.
Finally, It is shown as signals with high frequency values
return values with more illumination level independence.
\end{abstract}

\begin{keyword}
Biospeckle laser \sep 
Biospeckle index \sep 
Biospeckle signal\sep 
Biological activity \sep
Dynamic speckle \sep  
Backscattering.
\end{keyword}

\end{frontmatter}

\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
In the literature we can found a work \cite{RIVERA2017144} that show as some speckle indexes
have a frequency filter behavior; by example, we have the $AVD$ \cite{avd} and 
$IM$ \cite{ARIZAGA1999163} index, that they filter
the information like a first order high pass filter with cut-off in the middle
of normalized frequency band. For this reason, It is important analyze how,
the chosen frequency band, alter the result of selected index.
By other side others works 
\textcolor{red}{[cita] (acho tinha um artigo de kefir que tinha problemas de iluminacao)} 
show the problem of
made a speckle analysis with the presence of variation of illumination, because
the most of biospeckle indexes in the literature are influenced in your values
by the use of a determinate illumination level.
Thus, the present work searches establish a relation between the frequency band used
and the speckle index; specifically here will be studied the dependence of
the temporal speckle deviation matrix \cite{Nothdurft:05} with the illumination level.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System description}
\label{sec:description}

\subsection{Obtaining data packages in the test over an ink sample}
\label{sec:descriptionink}
The Fig. \ref{fig:system} shows the system diagram of the ink sample test; in It, we can see as
a red laser was pointed to an ink sample, the drying process is monitored by a digital camera;
the images are collected receiving two different illumination levels, because these 
are obtained using a neutral 
density lens between the ink sample and the laser, covering partially the view angle of the laser.
The images in each data package
are sampled with a frequency of $F_s=$\textcolor{red}{[[[12.5]]]} hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{System description.}
\label{fig:system}
\end{figure}
In each one of the $11$ packages were selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with black lines in the Fig. \ref{fig:regions}. In the right side of the figure  we have the
portion of image that was altered by the neutral density lens. The figure represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}. Being this value associated in the literature with
the illumination quantity in the surface of sample \cite{Nothdurft:05}; corresponding thus high values of $\mu$
to places with more illumination. 
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}

\subsection{Obtaining data packages in the test over a paper piece}
\label{sec:descriptionpaper}
The test over a paper piece has a similar configuration that seen in
the Fig. \ref{fig:system} with the difference that in the paper piece test is not used
the neutral density lens; thus It is collected one data package
sampled with a frequency of $F_s=$\textcolor{red}{[[[12.5]]]} hertz, being 
collected in total $N=129$ images of 640$\times$480 pixels.
The Fig. \ref{fig:meanpaper} represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}; thus, it is easy to see how the
illumination level of laser over the paper has a elliptical form being it higher 
in the centroid close to the image top.
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall.eps}
\caption{Light intensity distribution in the paper piece test.}
\label{fig:meanpaper}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical analysis}
\label{sec:analysis}

\subsection{Data package filtering in three frequency band}
\label{subsec:firfilters}
Each data package or sub package ($P_T$) goes through of a filter bank with 4 outputs  having each
one a different type of processing, the first output is trivial because it
leave pass the information freely, this package is called of $P_T$, the others 3 processing types
return  signals, filter by frequency band; thus, 
we have the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
the band between $[\frac{1}{3},\frac{2}{3}]\frac{F_s}{2}$ (intermediate frequencies) and
the band between $[\frac{2}{3},1]\frac{F_s}{2}$ (high frequencies); obtaining at end, the packages 
$P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in the  Fig. \ref{fig:firfilters}.
Internally the obtaining of the filtered packages are realized using in cascade
two low pass Finite Impulse Response ($FIR$) filters of order $32$, so that
the sum of signals $P_X+P_Y+P_Z=P_T$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.55\columnwidth]{firfilters.eps}
\caption{Filtering of data packages.}
\label{fig:firfilters}
\end{figure}

\subsection{Temporal speckle deviation matrix}
\label{subsec:deviation}
The calculus of the temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05} 
uses as input, the $N$ images of a data package.
We designate to each image, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, being $k$ an integer;
thus, to get the value $\sigma$, 
 it is necessary to get 
the matrix $\sigma$ as seen in the Equation \ref{eq:cont2}, 
\begin{equation}\label{eq:cont2}
\sigma  = \sqrt{ \frac{1}{N} \sum_{k=1}^{N} (\mathbf{I}_{k}-\mu)^2  },
\end{equation}
being that, the value $\mu$ can be calculated as, 
\begin{equation}\label{eq:cont1}
\mu =  \frac{1}{N} \sum_{k=1}^{N} \mathbf{I}_{k},
\end{equation}

Additionally, can be defined the temporal speckle deviation index, $\bar{\sigma}=<\sigma>$, as the mean value
of all elements in $\sigma$, being $<.>$ the mean spatial operator.
%And $\sigma_p$ as any value of an element in  $\sigma$.

\subsection{Datapack processing in the ink drying test }
\label{subsec:numprocink}

As explicated in the Sec. \ref{sec:descriptionink} we have in the ink drying test, analysis regions  with
two levels of illumination in each data packages; thus, we  separate each package in two sub package
(left and right), representing each one the regions shown in the Fig. \ref{fig:regions}.
These sub packages are filtered following the process explicated in the Sec. \ref{subsec:firfilters},
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering.eps}
\caption{Filtering of data packages.}
\label{fig:filtering}
\end{figure}
Immediately later of obtained these filtered packages, over each one of these
is calculated the temporal speckle deviation matrix and in base of this result are obtained the 
temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
$\bar{\sigma}_Z$. The procedure to obtain these values is 
explicated in the Sec. \ref{subsec:deviation}.

\subsection{Statistical analysis of relation between the matrices $\sigma$ and $\mu$}
\label{subsec:statistical}
We define $\sigma_i$ and $\mu_i$
as the values in the $i-th$ position in the $\sigma$  
and $\mu$ matrices, respectively; also define $\mu_p$
as any element value in  $\mu$.
And finally we define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
as the set of all $\sigma_i$  values given that $\mu_i\equiv\mu_p$.
With all these in mint we calculate the vectors $L_p$, $\sigma_p$ and
$e_p$ using all the $\mu_p$ values, according the next description.
\begin{itemize}
 \item $L_p(\mu_p)=card\left(S_{\mu_p}\right)$,  being $L_p(\mu_p)$ the number of elements
 in the set $S_{\mu_p}$ and $card(.)$ the cardinality function operator.
 \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, being $\sigma_p(\mu_p)$
 the mean value of elements in the set $S_{\mu_p}$ and $mean(.)$ represents the mean value function operator.
 \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, being $\e_p(\mu_p)$
 the standard  deviation value of elements in the set $S_{\mu_p}$ and $std(.)$ represents the standard deviation function operator.
\end{itemize}
In the practice only will be take in count in the vectors, values of $\mu_p$
with a $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.

\subsection{Datapack processing in the paper piece test }
\label{subsec:numprocink}

As explicated in the Sec. \ref{sec:descriptionpaper}, in this test we have one data package;
this package is filtered following the process explicated in the Sec. \ref{subsec:firfilters},
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$,
over each one of these filtered packages 
are calculated the temporal speckle mean matrix and the 
temporal speckle deviation matrix, as can be seen in the Fig. \ref{fig:filtering2}.

\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering2.eps}
\caption{Filtering of data package in paper piece test.}
\label{fig:filtering2}
\end{figure}

In base of these results are made statistical analysis to obtain the 
vectors $\sigma_p$, $\mu_p$, $e_p$ to each one of bands. 
The procedure to obtain these values is explicated in the Sec. \ref{subsec:statistical}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical results} 
\label{sec:numerical}

\subsection{Numerical results in the ink drying test} 
\label{subsec:numericalink}
In the Fig. \ref{fig:numerical} we can see the result of data packages processing 
 in the ink drying test. The Fig. \ref{fig:allink}
represent the $\bar{\sigma}_T$ value in two light intensity levels, It is calculates over the package $P_T$
trough the time, and use the complete frequency band.
The Fig. \ref{fig:stdxink}
represent the $\bar{\sigma}_X$ value in two light intensity levels, It is calculates over the package $P_X$
trough the time, and use the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
The Fig. \ref{fig:stdyink}
represent the $\bar{\sigma}_Y$ value in two light intensity levels, It is calculates over the package $P_Y$
trough the time, and use the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
And the Fig. \ref{fig:stdzink}
represent the $\bar{\sigma}_Z$ value in two light intensity levels, It is calculates over the package $P_Z$
trough the time, and use the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-all.eps}
	\caption{$\bar{\sigma}_T$ value through  the time.}
        \label{fig:allink}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandx.eps}
	\caption{$\bar{\sigma}_X$ value through  the time.}
        \label{fig:stdxink}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandy.eps}
	\caption{$\bar{\sigma}_Y$ value through  the time.}
        \label{fig:stdyink}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandz.eps}
	\caption{$\bar{\sigma}_Z$ value through  the time.}
        \label{fig:stdzink}
    \end{subfigure}

\caption{Numerical results in the ink drying test.}\label{fig:numerical}
\end{figure}
As can be seen, when analyze the index over the complete frequency band (Fig. \ref{fig:allink}),
we have different results to both illuminations levels, being that the index
value It is major in the left side,that is the side with most illumination. This 
indicates a positive influence of illumination level in the index value.
By other side, if we observe the figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
we can perceive as the index values from different
illuminations  turn most similar with the grow of frequency.
being greater this similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
Thus the similarity is limit by the sampling frequency used.

Finally It is important highlight that in an ink drying test, like the used here,
It is characterized by speckle signals with high frequencies in the begin time
of drying and  speckle signals with low frequencies at end, being gradual this frequency transition
until reach the limit of signal and to have only the noise of test.
So that, when in the figures It is observe a horizontal line in the index, these data
should not be use in the comparisons, even if they are similar, given that these
only are show the noise of test. By example, in the Fig. \ref{fig:stdzink}
we filter so that only have high frequency signals; later, we know that these only happen
in the begin of drying process, and in the figure this happen from 0 until
the 50 minutes and later only have a similar horizontal line in both illuminations.
This indicates that the comparisons of index illumination independence
only should be made between these minutes because out this range we will be using
the noise of test in the comparisons.

\subsection{Numerical results in the paper piece test} 
\label{subsec:numericalpaper}
In the Fig. \ref{fig:papelstd} we can see the result of the processing 
the data packages in the paper piece test. The Fig. \ref{fig:papelall}
represent the $\sigma_T$ matrix that use the complete frequency band.
The Fig. \ref{fig:papelstd_stdx}
represent the $\sigma_X$ matrix that use the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
The Fig. \ref{fig:papelstd_stdy}
represent the $\sigma_Y$ matrix that use the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
And the Fig. \ref{fig:papelstd_stdz} 
represent the $\sigma_Z$ matrix that use the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.485\textwidth}
        \includegraphics[width=\textwidth]{stdall.eps}
	\caption{$\sigma_T$ matrix over the complete frequency band.}
        \label{fig:papelall}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.465\textwidth}
        \includegraphics[width=\textwidth]{stdx.eps}
	\caption{$\sigma_X$ matrix over the inferior third of the frequency band.}
        \label{fig:papelstd_stdx}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdy.eps}
	\caption{$\sigma_Y$ matrix over the middle third of the frequency band.}
        \label{fig:papelstd_stdy}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdz.eps}
	\caption{$\sigma_Z$ matrix over the superior third of the frequency band.}
        \label{fig:papelstd_stdz}
    \end{subfigure}

    \caption{Temporal speckle deviation matrix of paper piece.}
    \label{fig:papelstd}
\end{figure}

In the next group of graphics we analysis the relation between a value $\sigma_p$,
in the $\sigma$ matrix, with a value $\mu_p$, in the $\mu$ matrix, to all
frequency bands. 
These analysis have importance because  the value $\mu_p$
is related with the illumination level in the surface of sample \cite{Nothdurft:05}
and the color or material of sample. Thus, when we choose $\mu_p$  as reference variable
in a homogeneous sample,  
in true we choose indirectly the illumination level in the surface.
In these sense, the Figs. \ref{fig:papelilllevel}, \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy}
and \ref{fig:illlevel_stdz} show the variables $\sigma_p$, $e_p$ and $L_p$ in function
of  $\mu_p$, to the case of the complete frequency band, the inferior third of the frequency band,
the middle third of the frequency band and the superior third of the frequency band,
respectively in each sub figure. It is import to note that $e_p$ ever is graph as percentage
in the relation to the value $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdall_curve.eps}
	\caption{Analysis in the complete frequency band.}
        \label{fig:illlevel_all}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdx_curve.eps}
	\caption{Analysis in the inferior third of the frequency band.}
        \label{fig:illlevel_stdx}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdy_curve.eps}
	\caption{Analysis in the middle third of the frequency band.}
        \label{fig:illlevel_stdy}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdz_curve.eps}
	\caption{Analysis in the superior third of the frequency band.}
        \label{fig:illlevel_stdz}
    \end{subfigure}

    \caption{Relation between the standard deviation value and the illumination level in a paper piece.}
    \label{fig:papelilllevel}
\end{figure}

In all these results we hope see a homogeneous tend in the index values,
in all spatial positions, because has been analyzed an homogeneous paper piece.
Keeping this in mind, in the Fig. \ref{fig:papelall} we observe
a  slightly homogeneity in the values because exist a variability in 
the result in some regions, this is most evident if we analyze the Fig. \ref{fig:illlevel_all}
where observe as change the value $\sigma_p$ in relation to the value $\mu_p$,
so that
$\sigma_p$ is around of $5.5$ with changes that depended of illumination level $\mu_p$,
but even to a specific value $\mu_p$ exist much variability in the expected value of $\sigma_p$,
having a $e_p$ around of $12\%$ in the best case. In other cases in the Figs. \ref{fig:illlevel_stdx},
\ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz}. We observe a linear ascendant relation
between $\sigma_p$ and $\mu_p$, being that the slope decreases with 
the increase of the frequency band. As can be seen in the Fig. \ref{fig:illlevel_stdz}
where the variations in $\mu_p$  only slightly influence to $\sigma_p$ and the error $e_p$
can be of $5\%$ when the illumination is maximum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

In this work were presented comparisons between the values of the temporal speckle 
deviation index to 3 different frequency bands of the speckle signal and
different illuminations levels, in a
dynamic laser speckle analysis, the results shown as the influence of illumination level over
the index decreases with the use of signals with high frequency bands.

\section{Acknowledgment}
We wish to acknowledge the partial financial support for this study provided by the $CAPES$ 
scholarship
$PNPD$ Program, $FAPEMIG$ and $CNPQ$.

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\section{Bibliography}
\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

%----------------------------------------------------------------------------------------

\end{document}

### 2018-03-11 article/images/dialatex2eps.sh

@@ -1,0 +1,44 @@
+#!/bin/bash
+
+
+FILENAME=( "filtering" "filtering2" "firfilters")
+
+for i in ${FILENAME[@]}; 
+do  
+    echo XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+    echo $i
+    echo XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+
+    dia $i.dia -t mp --export=$i.mp
+
+    sed -i '/\documentclass{minimal}/a \
+    \\usepackage{amsmath,amssymb}' $i.mp
+
+    mpost  -tex=latex -interaction=nonstopmode $i.mp
+
+    echo "\documentclass{article}
+    \pagestyle{empty}
+    \usepackage{graphicx}
+    \begin{document}
+    \includegraphics[width=\textwidth]{"$i.1"}
+    \end{document}" > temporallatex-$i.tex
+
+
+    latex temporallatex-$i.tex
+    dvips -E -o $i.eps temporallatex-$i
+
+    rm -f $i.log
+    rm -f $i.mpx
+    rm -f $i.mp
+    rm -f $i.1
+
+    rm -f temporallatex-$i.tex
+    rm -f temporallatex-$i.aux  
+    rm -f temporallatex-$i.log  
+    rm -f temporallatex-$i.dvi
+
+    #convert -density 400 $i.eps -flatten $i.png
+
+    #rm -f $i.eps
+
+done

### 2018-03-11 mcode/func_curva_lux.m

@@ -1,0 +1,125 @@
+function [D E Dx Ex Dy Ey Dz Ez OUTPUT]=func_curva_lux(DIRECTORY,PATTERN,NUMIMGI,NUMIMGF,POIN2D)
+    close all
+
+    NSAMPLES = 100;
+    if( 2 ~= size(POIN2D,1) )
+        error('Os pontos devem ser 2 solamente')
+    end
+
+
+    POIN2D=round(POIN2D);
+    POIN2D(:,1)=sort(POIN2D(:,1));
+    POIN2D(:,2)=sort(POIN2D(:,2));
+
+    AA=[POIN2D(1,1) POIN2D(1,2)];
+    CC=[POIN2D(2,1) POIN2D(2,2)];
+    BB=[POIN2D(1,1) POIN2D(2,2)];
+    DD=[POIN2D(2,1) POIN2D(1,2)];
+
+    POINT= [AA; BB; CC ;DD];
+
+    IMAGESDIR=DIRECTORY;
+    OUTPUT   =fullfile(IMAGESDIR,'output_func_curva_lux');
+    rmdir(OUTPUT);
+    mkdir(OUTPUT);
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %close all;
+    DATAT =datapack(IMAGESDIR,PATTERN,NUMIMGI,NUMIMGF,'bmp');
+    [C D E]=stdcont(DATAT,'off');
+
+    FONTSIZE=20;
+
+    figure(1);
+    imagesc(E);
+    colorbar();
+    colormap(jet);
+    title('All band Mean')
+    print(figure(1),fullfile(OUTPUT,'meanall.eps'),'-depsc',['-F:',int2str(FONTSIZE)]);
+
+    figure(2);
+    imagesc(D);
+    colorbar();
+    colormap(jet);
+    title('All band Std')
+    print(figure(2),fullfile(OUTPUT,'stdall.eps'),'-depsc',['-F:',int2str(FONTSIZE)]);
+
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    figure(1);
+    NNN=4;
+    for JJ=1:NNN
+        hold('on');
[…]

### 2018-03-11 mcode/prog_multiple.m

@@ -1,0 +1,76 @@
+%
+close all
+pkg load bsltl
+pkg load signal
+
+%addpath(genpath('/media/fernando/FER8G-BTRFS/PROGRAMACION/NONGNU.ORG/BSLTL/BSLTL-PKG/bsltl-pkg/bsltl/inst/mfiles'))
+
+%close all
+addpath('funcs2');
+
+
+
+
+
+%%
+
+PASTA={'0min', '10min', '20min', '30min', '40min', '50min', '60min', '75min', '105min', '120min', '150min' };
+TEMPO=[0 , 10, 20, 30, 40, 50, 60, 75,105,120,150];
+
+
+NN=length(PASTA);
+DIRECTORY= '/media/fernando/Hitachi/Resultados/Novos-dados-argentina/';
+PATTERN  = '%d';
+NUMIMGI=1;
+NUMIMGF=400;
+
+%POINT=[[50 10];[300 210]];
+POINT=[[50 260];[300 460]];
+%PRENAME='left-'
+PRENAME='right-'
+
+MEAN_D =zeros(1,NN);
+MEAN_DX=zeros(1,NN);
+MEAN_DY=zeros(1,NN);
+MEAN_DZ=zeros(1,NN);
+
+for II=1:NN
+    LOCALDIR=fullfile(DIRECTORY,PASTA{II})
+    [D E Dx Ex Dy Ey Dz Ez OUTPUT]=func_curva_lux(LOCALDIR,PATTERN,NUMIMGI,NUMIMGF,POINT);
+    MEAN_D (II)=mean(mean(D (POINT(:,1)',POINT(:,2)')));
+    MEAN_DX(II)=mean(mean(Dx(POINT(:,1)',POINT(:,2)')));
+    MEAN_DY(II)=mean(mean(Dy(POINT(:,1)',POINT(:,2)')));
+    MEAN_DZ(II)=mean(mean(Dz(POINT(:,1)',POINT(:,2)')));
+end
+
+close all
+FONTSIZE=20;
+
+
+mkdir([PRENAME 'prog_multiple'])
+
+
+figure(1)
+plot(TEMPO,MEAN_D)
+title('STD in time')
+xlabel('Time in min')
+ylabel('STD')
+print(figure(1),[[PRENAME 'prog_multiple'] '/meanall.eps'],'-depsc',['-F:',int2str(FONTSIZE)]);
+
[…]

### 2018-03-11 mcode/prog_multiple_plot.m

@@ -1,0 +1,41 @@
+%
+FONTSIZE=20;
+DATAL=load('left-data.dat');
+DATAR=load('right-data.dat');
+
+DATAL = DATAL.DATA;
+DATAR = DATAR.DATA;
+
+TEMPO=[0 , 10, 20, 30, 40, 50, 60, 75,105,120,150];
+
+figure(1)
+plot(TEMPO,DATAL.MEAN_D,'-o',TEMPO,DATAR.MEAN_D,'-*')
+title('<\sigma_T> in time')
+xlabel('Time in min')
+ylabel('<\sigma_T>')
+legend('LEFT','RIGHT');
+print(figure(1),'std-all.eps','-depsc',['-F:',int2str(FONTSIZE)]);
+
+figure(2)
+plot(TEMPO,DATAL.MEAN_DX,'-o',TEMPO,DATAR.MEAN_DX,'-*')
+title('<\sigma_X> in time: 0 - 0.333')
+xlabel('Time in min')
+ylabel('<\sigma_X>')
+legend('LEFT','RIGHT');
+print(figure(2),'std-bandx.eps','-depsc',['-F:',int2str(FONTSIZE)]);
+
+figure(3)
+plot(TEMPO,DATAL.MEAN_DY,'-o',TEMPO,DATAR.MEAN_DY,'-*')
+title('<\sigma_Y> in time: 0.333 - 0.666')
+xlabel('Time in min')
+ylabel('<\sigma_Y>')
+legend('LEFT','RIGHT');
+print(figure(3),'std-bandy.eps','-depsc',['-F:',int2str(FONTSIZE)]);
+
+figure(4)
+plot(TEMPO,DATAL.MEAN_DZ,'-o',TEMPO,DATAR.MEAN_DZ,'-*')
+title('<\sigma_Z> in time: 0.666 - 1.000')
+xlabel('Time in min')
+ylabel('<\sigma_Z>')
+legend('LEFT','RIGHT');
+print(figure(4),'std-bandz.eps','-depsc',['-F:',int2str(FONTSIZE)]);

### 2018-03-11 mcode2/funcs2/histograma_bsi.m

@@ -1,0 +1,72 @@
+function [LUX VAL ERR NN]=histograma_bsi(E1,D1,NSAMPLES,varargin )
+
+    if(nargin>3)
+        POINT=varargin{1};
+    else
+        POINT=[ 1, 1; ...
+                1, size(E1,2); ...
+                size(E1,1), size(E1,2); ...
+                size(E1,1), 1 ];
+    end
+
+
+    NLIN=size(E1,1);
+    NCOL=size(E1,2);
+
+    VAL2=cell(1,255);
+
+    MINL=min(POINT(:,1));
+    MINC=min(POINT(:,2));
+
+    MAXL=max(POINT(:,1));
+    MAXC=max(POINT(:,2));
+
+
+    for II=MINL:MAXL
+    for JJ=MINC:MAXC
+        in = inpolygon (II, JJ, POINT(:,1), POINT(:,2));
+        if in
+            ID=round(E1(II,JJ))+1;
+            VAL2{ID}(end+1)=D1(II,JJ);
+        end
+    end
+    fprintf('Working histograma_bsi line %3d of %3d\r',II,MAXL);
+    end
+    disp('');
+
+
+    N=0;
+    nn=zeros(1,255);
+    for II=2:255
+        nn(II)=length(VAL2{II});
+        if nn(II)>=NSAMPLES
+            N=N+1;
+        end
+    end
+
+    if(N==0)
+        disp(['Maximo numero de elementos:' num2str(max(nn)) ] );
+        disp(['Valor de limear:' num2str(NSAMPLES)] );
+        error('Numero de elementos LUX igual a 0')
+    end
+
+    LUX=zeros(1,N);
+    VAL=zeros(1,N);
+    ERR=zeros(1,N);
+    NN =zeros(1,N);
+
+    JJ=1;
+    for II=2:255
+        nn=length(VAL2{II});
+        if nn>=NSAMPLES
+            LUX(JJ)=II-1;
+            NN(JJ)=nn;
+            VAL(JJ)=mean(VAL2{II});
+            ERR(JJ)=std(VAL2{II});
+            JJ=JJ+1;
+        end
+    end
+
+
+
+end

### 2018-03-11 mcode2/funcs2/plot_histograma_bsi.m

@@ -1,0 +1,38 @@
+function [HA1 HA2 HA3 LUX VAL ERR NSAMPLES]=plot_histograma_bsi(E,D,NUMERO,varargin)
+
+if(nargin>3)
+    [LUX VAL ERR NSAMPLES]=histograma_bsi(E,D,NUMERO,varargin);
+else
+    [LUX VAL ERR NSAMPLES]=histograma_bsi(E,D,NUMERO);
+end
+
+MIN=min(LUX);
+MAX=max(LUX);
+
+
+gcf();
+
+subplot(3,1,1)
+errorbar(LUX,VAL,ERR), grid 
+xlabel('\mu_p')
+xlim([MIN MAX])
+ylim([0 10])
+%ylim([0 10])
+ylabel('\sigma_p')
+HA1=gca();
+
+subplot(3,1,2)
+plot(LUX,100*ERR./VAL,'-o')
+xlabel('\mu_p')
+xlim([MIN MAX])
+ylabel(' e_p (%)')
+HA2=gca();
+
+subplot(3,1,3)
+plot(LUX,NSAMPLES)
+xlim([MIN MAX])
+xlabel('\mu_p')
+ylabel('L_p')
+HA3=gca();
+
+end

### 2018-03-11 mcode2/prog_curva_lux.m

@@ -1,0 +1,110 @@
+%
+%pkg load bsltl
+close all
+pkg load bsltl
+%close all
+addpath('funcs2');
+
+pkg load signal
+
+FONTSIZE=16;
+
+DIRECTORY= '/media/fernando/Hitachi/DATA-OTROS/PAPEL/papel1';
+PATTERN  = '1%d';
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+IMAGESDIR=DIRECTORY;
+OUTPUT   =fullfile(IMAGESDIR,'output_prog_curva_lux');
+rmdir(OUTPUT);
+mkdir(OUTPUT);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%close all;
+DATAT =datapack(IMAGESDIR,PATTERN,0,128,'bmp');
+OFFSET=10;
+DATAT =DATAT((OFFSET+1):(end-OFFSET),(OFFSET+1):(end-OFFSET),:);
+[C D E]=stdcont(DATAT,'off');
+
+
+figure(1);
+imagesc(E);
+colorbar();
+colormap(jet);
+title('All band Mean')
+print(figure(1),fullfile(OUTPUT,'meanall.eps'),'-depsc',['-F:',int2str(FONTSIZE)]);
+
+figure(2);
+imagesc(D);
+colorbar();
+colormap(jet);
+title('All band Std')
+print(figure(2),fullfile(OUTPUT,'stdall.eps'),'-depsc',['-F:',int2str(FONTSIZE)]);
+
+
+
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+figure('Position', [100 100 600 800]);
+[HA1 HA2 HA3]=plot_histograma_bsi(E,D,200);
+title(HA1,['Complete frequency band '])
+print(gcf,fullfile(OUTPUT,'stdall_curve.eps'),'-depsc',['-F:',int2str(FONTSIZE)]);
+
[…]

### 2018-07-19 article/Make.sh
Ordenando para integrar com sharelatex

@@ -1,10 +1,0 @@
-#!/bin/bash
-
-latex  -interaction=nonstopmode  article_1.tex
-bibtex article_1
-latex  -interaction=nonstopmode  article_1.tex
-latex  -interaction=nonstopmode  article_1.tex
-
-dvips -o article_1.ps article_1.dvi
-ps2pdf article_1.ps article_1.pdf
-./Clean.sh

### 2018-07-19 article/article_1.tex
Agregando dados de sharelatex

@@
 
-\title{Illumination Level Independence in the Dynamic Laser Speckle Analysis}
+\title{Towards Illumination Level Independence in the Dynamic Laser Speckle Analysis}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the 
@@
 \section{Introduction}
-In the literature we can found a work \cite{RIVERA2017144} that show as some speckle indexes
-have a frequency filter behavior; by example, we have the $AVD$ \cite{avd} and 
-$IM$ \cite{ARIZAGA1999163} index, that they filter
-the information like a first order high pass filter with cut-off in the middle
-of normalized frequency band. For this reason, It is important analyze how,
-the chosen frequency band, alter the result of selected index.
-By other side others works 
-\textcolor{red}{[cita] (acho tinha um artigo de kefir que tinha problemas de iluminacao)} 
-show the problem of
-made a speckle analysis with the presence of variation of illumination, because
-the most of biospeckle indexes in the literature are influenced in your values
-by the use of a determinate illumination level.
-Thus, the present work searches establish a relation between the frequency band used
-and the speckle index; specifically here will be studied the dependence of
+Dynamic laser speckle is a phenomenon that is used to monitor changes in illuminated samples, and it can be measured by multiple indexes \cite{BSLTLBOOK}.
+The indexes are associated to the level of changes and could be expressed by numerical and or graphical outcomes that can be affected by filtering action during the image processing \cite{RIVERA2017144}.
+As an example, we have  the $AVD$ \cite{avd} and
+$IM$ \cite{ARIZAGA1999163} indexes, that filter
+the information present in the history of the speckle images like a first order high pass filter with a cut-off in the middle
+of the normalized frequency band. 
+For this reason, it is important to analyze how
+the chosen frequency band alters the result of selected index.
+By other side, there is still a limitation to make  speckle analysis in the presence of in-homogeneity of illumination, because
+the most of biospeckle indexes are influenced in their values
+by the use of a illumination level \cite{REIS2016}.
+The illumination level can vary regarding the profile of the sample, such as an apple \cite{KAZ:12a} or a very irregular surface present in a kefir \cite{kefir}. 
+It can also vary in accordance with the moisture present in the seed \cite{CARDOSO2011} due to the penetration of the light in the sample, or even when the color of the sample vary such as in the interface of cancer and normal tissues \cite{BCB+:12a}.
+And that is the reason to a continuous search for an adequate index, despite the fact there are many of them present in literature \cite{BSLTLBOOK}, but still without a solution to the independence of light intensity.
+The movement toward the portable equipment \cite{Bra:17}, reinforce the need to search the methods and its relation with the illumination. 
+Thus, the present work aimed to establish a relation between the frequency band used
+and the speckle index; particularly in the dependence of
 the temporal speckle deviation matrix \cite{Nothdurft:05} with the illumination level.
@@
 
-\subsection{Obtaining data packages in the test over an ink sample}
+\subsection{Data packages of drying ink}
 \label{sec:descriptionink}
-The Fig. \ref{fig:system} shows the system diagram of the ink sample test; in It, we can see as
-a red laser was pointed to an ink sample, the drying process is monitored by a digital camera;
-the images are collected receiving two different illumination levels, because these 
-are obtained using a neutral 
-density lens between the ink sample and the laser, covering partially the view angle of the laser.
-The images in each data package
-are sampled with a frequency of $F_s=$\textcolor{red}{[[[12.5]]]} hertz, being 
+Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
+a red laser was pointed to a layer of drying ink monitored by a digital camera;
+the images are collected receiving two different illumination levels, because of the neutral 
+density lens covering partially the laser beam \cite{REIS2016}.
+The images were placed in data packages
+are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
 collected $N=400$ images by package. In total were collected $11$ packages 
-(with two different illumination levels each one) at the minutes 
+(with the two different illumination levels each one) at the minutes 
 $0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
@@
 \includegraphics[width=0.65\columnwidth]{system.eps}
-\caption{System description.}
+\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of drying ink.}
 \label{fig:system}
 \end{figure}
-In each one of the $11$ packages were selected two regions, of $250\times200$ pixels, 
+In each image of the packages was selected two regions, of $250\times200$ pixels, 
 corresponding to the regions with two different illumination levels, 
-as shown with black lines in the Fig. \ref{fig:regions}. In the right side of the figure  we have the
+as shown with black lines in the Fig. \ref{fig:regions}. In the right side of the \ref{fig:regions}  we have the
 portion of image that was altered by the neutral density lens. The figure represents
@@
 \end{figure}
+\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\
 
-\subsection{Obtaining data packages in the test over a paper piece}
+\subsection{Data packages of a steady state paper}
 \label{sec:descriptionpaper}
-The test over a paper piece has a similar configuration that seen in
-the Fig. \ref{fig:system} with the difference that in the paper piece test is not used
-the neutral density lens; thus It is collected one data package
-sampled with a frequency of $F_s=$\textcolor{red}{[[[12.5]]]} hertz, being 
+The test over a steady state paper has a similar configuration that seen in
+the Fig. \ref{fig:system} with the the absence of 
+the neutral density lens.
+The phenomenon observed was the noise associated to the experimental configuration linked to the camera, to the resolution of the images and also the mechanical noise, and it was collected one data package
+sampled with a frequency of $F_s=$ 10 hertz, being 
 collected in total $N=129$ images of 640$\times$480 pixels.
@@
 showed in the Sec. \ref{subsec:deviation}; thus, it is easy to see how the
-illumination level of laser over the paper has a elliptical form being it higher 
-in the centroid close to the image top.
+illumination level of laser over the paper has an elliptical form being highest 
+close to the top of the image.
 \begin{figure}[h!]
@@
 \includegraphics[width=0.85\columnwidth]{meanall.eps}
-\caption{Light intensity distribution in the paper piece test.}
+\caption{Light intensity distribution in the paper piece test with highest illumination presented by red pixels and lowest by blue pixels.}
 \label{fig:meanpaper}
@@
 \label{subsec:firfilters}
-Each data package or sub package ($P_T$) goes through of a filter bank with 4 outputs  having each
+Each data package or sub package ($P_T$) went through of a filter bank with 4 outputs  having each
 one a different type of processing, the first output is trivial because it
-leave pass the information freely, this package is called of $P_T$, the others 3 processing types
-return  signals, filter by frequency band; thus, 
+lets to pass the information freely, this package is called of $P_T$, whilst the other 3 outcomes
+return  signals filtered by a frequency band; thus, 
 we have the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
@@
 $P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in the  Fig. \ref{fig:firfilters}.
-Internally the obtaining of the filtered packages are realized using in cascade
-two low pass Finite Impulse Response ($FIR$) filters of order $32$, so that
+The filtered packages of images were carried out using cascades
+of two low-pass Finite Impulse Response ($FIR$) filters of order $32$, so that
 the sum of signals $P_X+P_Y+P_Z=P_T$.
@@
 \label{subsec:deviation}
-The calculus of the temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05} 
-uses as input, the $N$ images of a data package.
+The temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05} 
+used to compare the results was obtained from the $N$ images of a data package.
 We designate to each image, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, being $k$ an integer;
@@
 
-Additionally, can be defined the temporal speckle deviation index, $\bar{\sigma}=<\sigma>$, as the mean value
+Additionally, the temporal speckle deviation index can be defined as $\bar{\sigma}=<\sigma>$, the mean value
 of all elements in $\sigma$, being $<.>$ the mean spatial operator.
@@
 
-\subsection{Datapack processing in the ink drying test }
+\subsection{Datapack processing in the test of a drying ink}
 \label{subsec:numprocink}
 
-As explicated in the Sec. \ref{sec:descriptionink} we have in the ink drying test, analysis regions  with
-two levels of illumination in each data packages; thus, we  separate each package in two sub package
-(left and right), representing each one the regions shown in the Fig. \ref{fig:regions}.
-These sub packages are filtered following the process explicated in the Sec. \ref{subsec:firfilters},
-obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$.
+We have in the drying ink regions  with
+two levels of illumination; thus, we  separated each package in two sub package
+(left and right), representing each one of the regions shown in the Fig. \ref{fig:regions}.
+These sub-packages were filtered,
+obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, that was used to obtain
 \begin{figure}[h!]
@@
 \end{figure}
-Immediately later of obtained these filtered packages, over each one of these
-is calculated the temporal speckle deviation matrix and in base of this result are obtained the 
+
+the temporal speckle deviation matrix and the 
 temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
-$\bar{\sigma}_Z$. The procedure to obtain these values is 
-explicated in the Sec. \ref{subsec:deviation}.
+$\bar{\sigma}_Z$.
 
@@
 \label{subsec:statistical}
-We define $\sigma_i$ and $\mu_i$
+We defined $\sigma_i$ and $\mu_i$
 as the values in the $i-th$ position in the $\sigma$  
-and $\mu$ matrices, respectively; also define $\mu_p$
+and $\mu$ matrices, respectively; we also defined $\mu_p$
 as any element value in  $\mu$.
-And finally we define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
+And we define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
 as the set of all $\sigma_i$  values given that $\mu_i\equiv\mu_p$.
-With all these in mint we calculate the vectors $L_p$, $\sigma_p$ and
-$e_p$ using all the $\mu_p$ values, according the next description.
+Then, we obtained the vectors $L_p$, $\sigma_p$ and
+$e_p$ using all the $\mu_p$ values, according to:
 \begin{itemize}
@@
  \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, being $\sigma_p(\mu_p)$
- the mean value of elements in the set $S_{\mu_p}$ and $mean(.)$ represents the mean value function operator.
+ the mean value of elements in the set $S_{\mu_p}$ with $mean(.)$ representing the mean value function operator.
  \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, being $\e_p(\mu_p)$
- the standard  deviation value of elements in the set $S_{\mu_p}$ and $std(.)$ represents the standard deviation function operator.
+ the standard  deviation value of elements in the set $S_{\mu_p}$ with $std(.)$ representing the standard deviation function operator.
 \end{itemize}
-In the practice only will be take in count in the vectors, values of $\mu_p$
+In practice only will be taken the vectors, values of $\mu_p$
 with a $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.
 
-\subsection{Datapack processing in the paper piece test }
+\subsection{Datapack processing in the test of a steady state paper}
 \label{subsec:numprocink}
 
-As explicated in the Sec. \ref{sec:descriptionpaper}, in this test we have one data package;
-this package is filtered following the process explicated in the Sec. \ref{subsec:firfilters},
-obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$,
-over each one of these filtered packages 
-are calculated the temporal speckle mean matrix and the 
+In this test we have one data package that was filtered (\ref{fig:filtering2}) obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
 temporal speckle deviation matrix, as can be seen in the Fig. \ref{fig:filtering2}.
@@
 \includegraphics[width=0.65\columnwidth]{filtering2.eps}
-\caption{Filtering of data package in paper piece test.}
+\caption{Filtering of data package in the steady paper obtaining the mean and the deviation outcomes.}
 \label{fig:filtering2}
 \end{figure}
-
-In base of these results are made statistical analysis to obtain the 
-vectors $\sigma_p$, $\mu_p$, $e_p$ to each one of bands. 
-The procedure to obtain these values is explicated in the Sec. \ref{subsec:statistical}.
 
@@
 
-\subsection{Numerical results in the ink drying test} 
+\subsection{Numerical results o the drying ink test} 
 \label{subsec:numericalink}
-In the Fig. \ref{fig:numerical} we can see the result of data packages processing 
- in the ink drying test. The Fig. \ref{fig:allink}
-represent the $\bar{\sigma}_T$ value in two light intensity levels, It is calculates over the package $P_T$
-trough the time, and use the complete frequency band.
+In the Fig. \ref{fig:numerical}, we can see the result of processing 
+ the drying ink test under the dynamic laser speckle index (DLSI) in two areas with different level of illumination. The Fig. \ref{fig:allink}
+represents the $\bar{\sigma}_T$ value in two light intensity levels, and it is done using the package $P_T$
+trough the time, with the complete frequency bands.
 The Fig. \ref{fig:stdxink}
-represent the $\bar{\sigma}_X$ value in two light intensity levels, It is calculates over the package $P_X$
-trough the time, and use the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
+represents the $\bar{\sigma}_X$ value in two light intensity levels, an it is done using the package $P_X$
+trough the time, with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
 The Fig. \ref{fig:stdyink}
-represent the $\bar{\sigma}_Y$ value in two light intensity levels, It is calculates over the package $P_Y$
-trough the time, and use the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
+represents the $\bar{\sigma}_Y$ value in two light intensity levels, and it is done using the package $P_Y$
+trough the time, with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
 And the Fig. \ref{fig:stdzink}
-represent the $\bar{\sigma}_Z$ value in two light intensity levels, It is calculates over the package $P_Z$
-trough the time, and use the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
+represent the $\bar{\sigma}_Z$ value in two light intensity levels, and it is done using the package $P_Z$
+trough the time, with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
 \begin{figure}[h!]
@@
 \end{figure}
-As can be seen, when analyze the index over the complete frequency band (Fig. \ref{fig:allink}),
-we have different results to both illuminations levels, being that the index
-value It is major in the left side,that is the side with most illumination. This 
+As can be seen, when we analyzed the index over the complete frequency band (Fig. \ref{fig:allink}),
+we had different results to both illuminations levels, being high in the left side,that is the side with most illumination. This 
 indicates a positive influence of illumination level in the index value.
-By other side, if we observe the figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
-we can perceive as the index values from different
-illuminations  turn most similar with the grow of frequency.
-being greater this similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
-Thus the similarity is limit by the sampling frequency used.
+By other side, if we observe the Figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink}
+we can see how the index values from different
+illuminations  was similar to the frequency level,
+being greatest similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
+Thus the similarity is limited by the sampling rate used.
 
-Finally It is important highlight that in an ink drying test, like the used here,
-It is characterized by speckle signals with high frequencies in the begin time
-of drying and  speckle signals with low frequencies at end, being gradual this frequency transition
-until reach the limit of signal and to have only the noise of test.
-So that, when in the figures It is observe a horizontal line in the index, these data
-should not be use in the comparisons, even if they are similar, given that these
-only are show the noise of test. By example, in the Fig. \ref{fig:stdzink}
-we filter so that only have high frequency signals; later, we know that these only happen
-in the begin of drying process, and in the figure this happen from 0 until
-the 50 minutes and later only have a similar horizontal line in both illuminations.
+Finally, it is important to highlight that in the drying ink test, the information from the dynamic laser speckle is linked to high frequencies in the beginning of the drying process and  speckle signals with low frequencies at end, being gradual the transition
+until reach the lowest level of signal with only the noise of test.
+In Figure \ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a transition of state with the stabilization of the DLSI.
+Thus, after this point, one has only the inner noise of the system influencing the DLSI.
+
 This indicates that the comparisons of index illumination independence
-only should be made between these minutes because out this range we will be using
-the noise of test in the comparisons.
+only should be made between the first minutes because out this range we will be using high contribution of 
+the noise as outcome.
 
-\subsection{Numerical results in the paper piece test} 
+\subsection{Numerical results of a steady paper under laser light} 
 \label{subsec:numericalpaper}
-In the Fig. \ref{fig:papelstd} we can see the result of the processing 
-the data packages in the paper piece test. The Fig. \ref{fig:papelall}
-represent the $\sigma_T$ matrix that use the complete frequency band.
-The Fig. \ref{fig:papelstd_stdx}
-represent the $\sigma_X$ matrix that use the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
-The Fig. \ref{fig:papelstd_stdy}
-represent the $\sigma_Y$ matrix that use the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
-And the Fig. \ref{fig:papelstd_stdz} 
-represent the $\sigma_Z$ matrix that use the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
+In the Fig. \ref{fig:papelstd} we can see the result of data processing from the steady
+ paper under dynamic laser speckle phenomenon considering an homogeneous illumination and using the standard deviation $\sigma$ as a dynamic laser speckle index (DLSI). Fig. \ref{fig:papelall}
+represents the $\sigma_T$ matrix with the complete frequency band, while Fig. \ref{fig:papelstd_stdx}
+represents the $\sigma_X$ matrix with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
+Fig. \ref{fig:papelstd_stdy} represents the $\sigma_Y$ matrix with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz, and Fig. \ref{fig:papelstd_stdz} 
+represents the $\sigma_Z$ matrix with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
 \begin{figure}[h!]
@@
 
-In the next group of graphics we analysis the relation between a value $\sigma_p$,
-in the $\sigma$ matrix, with a value $\mu_p$, in the $\mu$ matrix, to all
-frequency bands. 
-These analysis have importance because  the value $\mu_p$
-is related with the illumination level in the surface of sample \cite{Nothdurft:05}
-and the color or material of sample. Thus, when we choose $\mu_p$  as reference variable
+In Figure \ref{fig:papelilllevel} we present the relation between an average value of $\sigma_p$,
+in the $\sigma$ matrix, with a value $\mu_p$ (mean value representing the illumination level) of the $\mu$ matrix, to all frequency bands, the value $\mu_p$
+is related to the illumination level in the surface of the sample \cite{Nothdurft:05}
+and the color or material of sample. Thus, when we choose $\mu_p$  as reference 
 in a homogeneous sample,  
 in true we choose indirectly the illumination level in the surface.
-In these sense, the Figs. \ref{fig:papelilllevel}, \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy}
-and \ref{fig:illlevel_stdz} show the variables $\sigma_p$, $e_p$ and $L_p$ in function
-of  $\mu_p$, to the case of the complete frequency band, the inferior third of the frequency band,
-the middle third of the frequency band and the superior third of the frequency band,
-respectively in each sub figure. It is import to note that $e_p$ ever is graph as percentage
-in the relation to the value $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$.
+Therefore, Fig. \ref{fig:papelilllevel} shows the variables $\sigma_p$, $e_p$ and $L_p$ in function
+of  $\mu_p$, to the case of the complete frequency band (\ref{fig:illlevel_all}), the inferior third of the frequency band (\ref{fig:illlevel_stdx}),
+the middle third of the frequency band (\ref{fig:illlevel_stdy}) and the superior third of the frequency band (\ref{fig:illlevel_stdz}).
+It is import to note that $e_p$ was plot as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$.
+
 \begin{figure}[h!]
@@
 
-    \caption{Relation between the standard deviation value and the illumination level in a paper piece.}
+    \caption{Relation between the standard deviation value and the illumination level in a steady paper under laser illumination.}
     \label{fig:papelilllevel}
@@
 
-In all these results we hope see a homogeneous tend in the index values,
-in all spatial positions, because has been analyzed an homogeneous paper piece.
-Keeping this in mind, in the Fig. \ref{fig:papelall} we observe
-a  slightly homogeneity in the values because exist a variability in 
-the result in some regions, this is most evident if we analyze the Fig. \ref{fig:illlevel_all}
-where observe as change the value $\sigma_p$ in relation to the value $\mu_p$,
-so that
-$\sigma_p$ is around of $5.5$ with changes that depended of illumination level $\mu_p$,
-but even to a specific value $\mu_p$ exist much variability in the expected value of $\sigma_p$,
-having a $e_p$ around of $12\%$ in the best case. In other cases in the Figs. \ref{fig:illlevel_stdx},
-\ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz}. We observe a linear ascendant relation
-between $\sigma_p$ and $\mu_p$, being that the slope decreases with 
-the increase of the frequency band. As can be seen in the Fig. \ref{fig:illlevel_stdz}
-where the variations in $\mu_p$  only slightly influence to $\sigma_p$ and the error $e_p$
-can be of $5\%$ when the illumination is maximum.
+In Figure \ref{fig:illlevel_all}, we observe the absence of tendency in the DLSI ($\sigma$) with respect to the intensity ($\mu$), i.e.
+with the increase of the $\mu$ value the standard deviation ($\sigma$) does not increase or decrease.
+However, around that constant there is a spread of $\sigma$ to each value of $\mu$ that creates an uncertainty in the outcome, and expressed by the error $e$.
+Figure \ref{fig:illlevel_all} represents the outcome from the data without filtering, thus with all frequencies.
+And the data is the noise present in the processes of illumination and image acquiring because the sample is a steady paper without changes in the scatterers of the laser light.
+Nevertheless, when we filter the signal (images in time), we can observe a change in the $\sigma$ with respect to the frequency range, unveiling the dependency of the DLSI to the level of illumination and its relation to the frequency.
+In Figure \ref{fig:illlevel_stdx}, in the inferior third of the frequency band, there is a tendency in the $\sigma$ value with respect to the level of light.
+The DLSI changes its value with respect to the illumination level, where in low illumination level one had highest error, with the $\sigma$ values spread around the mean value, and the error tending to zero when the level of light increased in some areas of the sample.
+The same behavior happened in the middle level of frequency band, and much less in the superior third of the frequency band, meaning that in the highest frequencies one had less influence of the level of light in the $\sigma$ values.
+Since the $\sigma$ DLSI does not filter the signal \cite{RIVERA2017144}, it must be considered this situation during the DLSI usage, as one can compromise the outcome by the influence of the illumination of the sample in the results.
+Dynamic laser speckle indexes can offer other index  options to circumvent that influence, for example, using the Absolute Value of the Differences DLSI and its variations \cite{BSLTLBOOK}.
 
@@
 In this work were presented comparisons between the values of the temporal speckle 
-deviation index to 3 different frequency bands of the speckle signal and
+deviation index to three different frequency bands of the speckle signal and
 different illuminations levels, in a
-dynamic laser speckle analysis, the results shown as the influence of illumination level over
-the index decreases with the use of signals with high frequency bands.
+dynamic laser speckle analysis. The results showed that the influence of the illumination level in
+the DLSI index decreases with the use of signals with high frequency bands.
 

### 2018-07-19 mcode2/prog_curva_lux.m
mejorando o grafico de std graphic
para que todos tengan la misma barra de colores

@@ -65,24 +65,29 @@ clear DATAT0
 
 
 [Cx Dx Ex]=stdcont(DATATx,'off');
+[Cy Dy Ey]=stdcont(DATATy,'off');
+[Cz Dz Ez]=stdcont(DATATz,'off');
+
+DMAX=max([max(max(Dx)) max(max(Dy)) max(max(Dz))  max(max(D))]);
+DMIN=min([min(min(Dx)) min(min(Dy)) min(min(Dz))  min(min(D))]);
+
 figure(7);
-imagesc(Dx);
+imagesc(Dx,[DMIN DMAX]);
 colorbar();
 title(['Std: filtered from 0.000 Fs/2 to 0.333 Fs/2 '])
 colormap(jet);
 print(figure(7),fullfile(OUTPUT,'stdx.eps'),'-depsc',['-F:',int2str(FONTSIZE)]);
 
-[Cy Dy Ey]=stdcont(DATATy,'off');
+
 figure(8);
-imagesc(Dy);
+imagesc(Dy,[DMIN DMAX]);
 colorbar();
 title(['Std: filtered from 0.333 Fs/2 to 0.666 Fs/2 '])
 colormap(jet);
 print(figure(8),fullfile(OUTPUT,'stdy.eps'),'-depsc',['-F:',int2str(FONTSIZE)]);
 
-[Cz Dz Ez]=stdcont(DATATz,'off');
 figure(9);
-imagesc(Dz);
+imagesc(Dz,[DMIN DMAX]);
 colorbar();
 title(['Std: filtered from 0.666 Fs/2 to 1.000 Fs/2 '])
 colormap(jet);

### 2018-10-03 article/article_1.tex
corrigiendo la imagen en blanco y negro

@@
 density lens covering partially the laser beam \cite{REIS2016}.
-The images were placed in data packages
+The images were placed in data packages and
 are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
@@
 \end{figure}
-In each image of the packages was selected two regions, of $250\times200$ pixels, 
+In each image of the packages were selected two regions, of $250\times200$ pixels, 
 corresponding to the regions with two different illumination levels, 
-as shown with black lines in the Fig. \ref{fig:regions}. In the right side of the \ref{fig:regions}  we have the
-portion of image that was altered by the neutral density lens. The figure represents
-with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
-showed in the Sec. \ref{subsec:deviation}. Being this value associated in the literature with
-the illumination quantity in the surface of sample \cite{Nothdurft:05}; corresponding thus high values of $\mu$
-to places with more illumination. 
+as shown with red lines in the Fig. \ref{fig:regions}. In the right side of the Fig. \ref{fig:regions}  we have the
+portion of image that was altered by the neutral density lens. 
 \begin{figure}[h!]
@@
 \end{figure}
-\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\
+%\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\
 

### 2018-10-24 article/article_1.tex
Modificando titulo
Corrigindo texto e refrencias

@@
 
-\title{Towards Illumination Level Independence in the Dynamic Laser Speckle Analysis}
+\title{Illumination Level Independence in the Dynamic Laser Speckle Analysis}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the 
@@
 % Group authors per affiliation:
-\author{-------- ------- ------}
-\author{-------- ------- ------}
+\author{Fernando Pujaico Rivera}
+\author{Roberto Alves Braga Jr.}
 
-% \author{Fernando Pujaico Rivera\fnref{myfootnote2}}
-% \author{Roberto Alves Braga Jr.\fnref{myfootnote1}}
-% \address{University Federal of Lavras, Lavras, Brazil}
-% \fntext[myfootnote2]{201518201@posgrad.ufla.br}
-% \fntext[myfootnote1]{robertobraga@deg.ufla.br }
+\address{University Federal of Lavras, Lavras, Brazil}
+\fntext[myfootnote2]{201518201@posgrad.ufla.br}
+\fntext[myfootnote1]{robertobraga@deg.ufla.br }
+%
 
@@
 Biological activity \sep
-Dynamic speckle \sep  
-Backscattering.
+Dynamic speckle 
 \end{keyword}
@@
 corresponding to the regions with two different illumination levels, 
-as shown with red lines in the Fig. \ref{fig:regions}. In the right side of the Fig. \ref{fig:regions}  we have the
+as shown with red lines in the Fig. \ref{fig:regions}; thus, in the right side of the Fig. \ref{fig:regions}  we have the
 portion of image that was altered by the neutral density lens. 
@@
 
-We have in the drying ink regions  with
+We have in the drying ink regions
 two levels of illumination; thus, we  separated each package in two sub package
@@
 \end{figure}
-
 the temporal speckle deviation matrix and the 
@@
 dynamic laser speckle analysis. The results showed that the influence of the illumination level in
-the DLSI index decreases with the use of signals with high frequency bands.
+the DLSI index, like the temporal speckle deviation 
+index, decreases with the use of signals with high frequency bands.
 

### 2019-07-22 article/article_1.tex
sumetido a Optics and Laser Technology
45% da revision

@@
 
-\journal{Optics Communications}
+\journal{Optics \& Laser Technology}
 
@@
 
-\title{Illumination Level Independence in the Dynamic Laser Speckle Analysis}
+\title{Analysis of Illumination Dependency  in the Dynamic Laser Speckle Analysis}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the 
@@
 
-\subsection{Data packages of drying ink}
+\subsection{Data packages of ink drying}
 \label{sec:descriptionink}
 Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
-a red laser was pointed to a layer of drying ink monitored by a digital camera;
+a red laser was pointed to a layer of ink drying monitored by a digital camera;
 the images are collected receiving two different illumination levels, because of the neutral 
@@
 \includegraphics[width=0.65\columnwidth]{system.eps}
-\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of drying ink.}
+\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of ink drying.}
 \label{fig:system}
@@
 corresponding to the regions with two different illumination levels, 
-as shown with red lines in the Fig. \ref{fig:regions}; thus, in the right side of the Fig. \ref{fig:regions}  we have the
+as shown with red lines in the Fig. \ref{fig:regions}; thus, 
+in the right side of the Fig. \ref{fig:regions}  we have the
 portion of image that was altered by the neutral density lens.
+Thus, the right side has low illumination, and
+the left side has a high illumination.
 \begin{figure}[h!]
@@
 \label{subsec:deviation}
-The temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05} 
-used to compare the results was obtained from the $N$ images of a data package.
-We designate to each image, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, being $k$ an integer;
-thus, to get the value $\sigma$, 
- it is necessary to get 
-the matrix $\sigma$ as seen in the Equation \ref{eq:cont2}, 
+The temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05},
+used to compare the results, it was obtained from the $N$ images of the data package $P$.
+We designate to each image matrix, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, 
+being $k$ an integer index that indicates that it is in use the $k$-th image $\mathbf{I}$ in the package.
+Thus, to get
+% the value $\bar{\sigma}$, it is necessary to get 
+the matrix $\sigma$ is used the Equation \ref{eq:cont2}, 
 \begin{equation}\label{eq:cont2}
@@
 \end{equation}
-being that, the value $\mu$ can be calculated as, 
+being that, the matrix $\mu$ can be calculated as, 
 \begin{equation}\label{eq:cont1}
-\mu =  \frac{1}{N} \sum_{k=1}^{N} \mathbf{I}_{k},
+\mu =  \frac{1}{N} \sum_{k=1}^{N} \mathbf{I}_{k}.
 \end{equation}
+In these last two equations, all the operations are matricial, 
+so that each element (aka pixel) $\mathbf{I}_{k}(i)$ in the matrix $\mathbf{I}_{k}$
+should be processed with your  counterpart $\mathbf{I}_{k+1}(i)$ in the matrix $\mathbf{I}_{k+1}$.
 
-Additionally, the temporal speckle deviation index can be defined as $\bar{\sigma}=<\sigma>$, the mean value
+Aditionally, the ``temporal speckle deviation index'' can be defined as $\bar{\sigma}=<\sigma>$, the mean value
 of all elements in $\sigma$, being $<.>$ the mean spatial operator.
@@
 
-\subsection{Datapack processing in the test of a drying ink}
+\subsection{Datapack processing in the test of a ink drying}
 \label{subsec:numprocink}
 
-We have in the drying ink regions
+We have in the ink drying regions
 two levels of illumination; thus, we  separated each package in two sub package
-(left and right), representing each one of the regions shown in the Fig. \ref{fig:regions}.
+(high and low illumination), representing each one of the regions shown in the Fig. \ref{fig:regions}.
 These sub-packages were filtered,
@@
 
-\subsection{Numerical results o the drying ink test} 
+\subsection{Numerical results o the ink drying test} 
 \label{subsec:numericalink}
 In the Fig. \ref{fig:numerical}, we can see the result of processing 
- the drying ink test under the dynamic laser speckle index (DLSI) in two areas with different level of illumination. The Fig. \ref{fig:allink}
+ the ink drying test under the dynamic laser speckle index (DLSI) in two areas with different level of illumination. The Fig. \ref{fig:allink}
 represents the $\bar{\sigma}_T$ value in two light intensity levels, and it is done using the package $P_T$
@@
 As can be seen, when we analyzed the index over the complete frequency band (Fig. \ref{fig:allink}),
-we had different results to both illuminations levels, being high in the left side,that is the side with most illumination. This 
+we had different results to both illuminations levels, being high in the left side of the Figure \ref{fig:regions} and low in the right. This 
 indicates a positive influence of illumination level in the index value.
@@
 
-Finally, it is important to highlight that in the drying ink test, the information from the dynamic laser speckle is linked to high frequencies in the beginning of the drying process and  speckle signals with low frequencies at end, being gradual the transition
+Finally, it is important to highlight that in the ink drying test, the information from the dynamic laser speckle is linked to high frequencies in the beginning of the drying process and  speckle signals with low frequencies at end, being gradual the transition
 until reach the lowest level of signal with only the noise of test.

### 2019-07-22 mcode/prog_multiple_plot.m

@@ -13,29 +13,29 @@ plot(TEMPO,DATAL.MEAN_D,'-o',TEMPO,DATAR.MEAN_D,'-*')
 title('<\sigma_T> in time')
 xlabel('Time in min')
 ylabel('<\sigma_T>')
-legend('LEFT','RIGHT');
+legend('HIGH','LOW');
 print(figure(1),'std-all.eps','-depsc',['-F:',int2str(FONTSIZE)]);
 
 figure(2)
 plot(TEMPO,DATAL.MEAN_DX,'-o',TEMPO,DATAR.MEAN_DX,'-*')
-title('<\sigma_X> in time: 0 - 0.333')
+title('<\sigma_X> in time: [0 - 0.333]Fs/2')
 xlabel('Time in min')
 ylabel('<\sigma_X>')
-legend('LEFT','RIGHT');
+legend('HIGH','LOW');
 print(figure(2),'std-bandx.eps','-depsc',['-F:',int2str(FONTSIZE)]);
 
 figure(3)
 plot(TEMPO,DATAL.MEAN_DY,'-o',TEMPO,DATAR.MEAN_DY,'-*')
-title('<\sigma_Y> in time: 0.333 - 0.666')
+title('<\sigma_Y> in time: [0.333 - 0.666]Fs/2')
 xlabel('Time in min')
 ylabel('<\sigma_Y>')
-legend('LEFT','RIGHT');
+legend('HIGH','LOW');
 print(figure(3),'std-bandy.eps','-depsc',['-F:',int2str(FONTSIZE)]);
 
 figure(4)
 plot(TEMPO,DATAL.MEAN_DZ,'-o',TEMPO,DATAR.MEAN_DZ,'-*')
-title('<\sigma_Z> in time: 0.666 - 1.000')
+title('<\sigma_Z> in time: [0.666 - 1.000]Fs/2')
 xlabel('Time in min')
 ylabel('<\sigma_Z>')
-legend('LEFT','RIGHT');
+legend('HIGH','LOW');
 print(figure(4),'std-bandz.eps','-depsc',['-F:',int2str(FONTSIZE)]);

### 2019-07-29 article/article_1.tex
casi listo

@@
 
+The sampling frequency used in the analysis of each test, 
+it was selected  trying to achieve the best speed of sampling to observe each phenomenon. 
+The purpose of these two tests is to observe the behavior of the indices in two cases; 
+one with an activity homogeneous level in space and time, and another with a heterogeneous activity.
+Thus, given that the paper activity test and the ink drying test are independent events, 
+without comparison between them self, your sampling frequencies are different.
+
 \subsection{Data package filtering in three frequency band}
@@
 Aditionally, the ``temporal speckle deviation index'' can be defined as $\bar{\sigma}=<\sigma>$, the mean value
-of all elements in $\sigma$, being $<.>$ the mean spatial operator.
+of all elements in the matrix $\sigma$, being $<.>$ the mean spatial operator.
 %And $\sigma_p$ as any value of an element in  $\sigma$.
+
+\subsection{Fujii matrix}
+\label{subsec:fujii}
+
+The Fujii matrix \cite{Fujii:87} is obtained from the $N$ images in the data package $P$.
+Similarly to the Section \ref{subsec:deviation}, 
+we designate to each image matrix, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$.
+Thus, to get the Fujii matrix is used the Equation \ref{eq:contFujii2}, 
+\begin{equation}\label{eq:contFujii2}
+Fujii  = \frac{1}{N-1} \sum_{k=1}^{N-1} \frac{|\mathbf{I}_{k}-\mathbf{I}_{k+1}|}{\mathbf{I}_{k}+\mathbf{I}_{k+1}}.
+\end{equation} 
+The  Fujii matrix mean value can be defined as $\overline{Fujii}=<Fujii>$, the mean value
+of all elements in the matrix $Fujii$.
+
+The Fujii matrix method represents the attempt to eliminate 
+the dependence on illumination level, in a speckle index.
+For this purpose, the method define the index as the mean value of the  first order high pass FIR filter, 
+$\mathbf{I}_{k}-\mathbf{I}_{k+1}$,
+whose values are corrected using an approximation of the intensity mean value, $\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
+This calculation aspect is the strong point of the method,
+because the Fujii method assumes that the increase in the speckle 
+light dynamic range ($\mathbf{I}_{k}-\mathbf{I}_{k+1}$) 
+will be linear in proportion with the increase in laser light ($\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$).
+This means that the method already uses high frequency components, of the speckle signal, 
+and discards those of low frequency, in addition  to attempting to correct or normalize the index value;
+and it is for these characteristics that it shows an acceptable performance, 
+to eliminate or decrease the dependence of the index with the laser intensity level.
+
+Additionally, it was defined the matrix $Fujii_{\alpha}$, 
+as the filtered version of package $P$ to the frequency band $\alpha$, following the Equation \ref{eq:contFujii3}.
+\begin{equation}\label{eq:contFujii3}
+Fujii_{\alpha}  = \frac{1}{N-1} \sum_{k=1}^{N-1} \frac{|\mathbf{(I_{\alpha})}_{k}-\mathbf{(I_{\alpha})}_{k+1}|}{\mathbf{I}_{k}+\mathbf{I}_{k+1}}.
+\end{equation}
+It is important to highlight that the numerator of the last equation, 
+use the signal in the matrices $\mathbf{(I_{\alpha})}_{k}$, that are filtered versions in the frequency band $\alpha$,
+of the matrix $\mathbf{I}_{k}$. 
+By other side, the denominator use the signal $\mathbf{I}_{k}$ which has the complete frequency band.
+This modification was implemented because the numerator, in the calculus, 
+represents or try be the mean value of speckle light intensity, 
+and it value tend to zero in frequency bands without 0 hertz components.
 
@@
 
+In the analysis, the minimum grayscale value, 
+it is fixed by the observable minimum light by the camera or the minimum speckle light intensity in the material analyzed.
+By other side, the maximum grayscale value, 
+it is fixed by the observable maximum light by the camera or the maximum speckle light intensity in the material analyzed.
+
 \subsection{Numerical results o the ink drying test} 
 \label{subsec:numericalink}
+
+The activity level analysis in the  ink drying process has as objective  analyze the behavior of dynamic a speckle index, 
+in the context of a process that change your characteristic in time.
+
 In the Fig. \ref{fig:numerical}, we can see the result of processing 
@@
 \end{figure}
+
 As can be seen, when we analyzed the index over the complete frequency band (Fig. \ref{fig:allink}),
@@
 \label{subsec:numericalpaper}
+
+%The paper piece test has a quasi-circular laser light distribution around a center and with decreasing light intensity with increasing the radius.
+
+Even if the activity level of a paper piece, 
+it  is considered as noise in the context of other tests, where takes place over it, 
+a process of greater activity and variant in time and space. 
+The speckle signal analysis of a paper piece, 
+that for this test we consider approximately homogeneous in its characteristics over time and space,
+will show us  the variation effect of an unique parameter, the light intensity on the dynamic speckle analysis.
+
 In the Fig. \ref{fig:papelstd} we can see the result of data processing from the steady
@@
 In Figure \ref{fig:papelilllevel} we present the relation between an average value of $\sigma_p$,
-in the $\sigma$ matrix, with a value $\mu_p$ (mean value representing the illumination level) of the $\mu$ matrix, to all frequency bands, the value $\mu_p$
+in the $\sigma$ matrix, with a value $\mu_p$ (mean value representing the illumination level) of the $\mu$ matrix, 
+in the complete frequency band, the value $\mu_p$
 is related to the illumination level in the surface of the sample \cite{Nothdurft:05}
@@
 the middle third of the frequency band (\ref{fig:illlevel_stdy}) and the superior third of the frequency band (\ref{fig:illlevel_stdz}).
-It is import to note that $e_p$ was plot as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$.
+It is import to note that $e_p$ was plot as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$,
+and $L_p$ is the histogram of the values in temporal speckle mean matrix, 
+given that the mean value is zero to any frequency band without the zero frequency,
+in the figures are showed the $L_p$ values of the complete frequency band, 
+with the objective of to have a reference of the illumination level and the number of pixels involved in the analysis.
 
@@
 
+\subsection{Numerical results using Fujii} 
+\label{subsec:vsfujii}
+
+The Figure \ref{fig:fujiiallink} shows the behavior of mean value to the Fujii matrix
+defined in the Equation \ref{eq:contFujii2}.
+The Figures \ref{fig:fujiixink}, \ref{fig:fujiiyink} and \ref{fig:fujiizink},
+show the behavior of mean value to the Fujii matrix defined in the Equation \ref{eq:contFujii3},
+to the cases of frequency bands X,Y and Z respectively. 
+\begin{figure}[!h]
+    \centering
+    \begin{subfigure}[b]{0.475\textwidth}
+        \includegraphics[width=\textwidth]{fujii-all.eps}
+	\caption{Fujii value in the complete band.}
+        \label{fig:fujiiallink}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.475\textwidth}
+        \includegraphics[width=\textwidth]{fujii-bandx.eps}
+	\caption{Fujii value in the X band.}
+        \label{fig:fujiixink}
+    \end{subfigure}
+    ~\\ 
+    \begin{subfigure}[b]{0.475\textwidth}
+        \includegraphics[width=\textwidth]{fujii-bandy.eps}
+	\caption{Fujii value in the Y band.}
+        \label{fig:fujiiyink}
+    \end{subfigure}
+  ~
+    \begin{subfigure}[b]{0.475\textwidth}
+        \includegraphics[width=\textwidth]{fujii-bandz.eps}
+	\caption{Fujii value in the Z band.}
+        \label{fig:fujiizink}
+    \end{subfigure}
+
+\caption{Numerical results in the ink drying test using Fujii index.}
+\label{fig:numericalvsfujii}
+\end{figure}
+
+As can be seen in all the images, the curves with more and less  illumination level are close,
+but there is no advantage in separating the signals by bands
+this can be explained if we analyze how the index synthesizes its value and we compares it with the images.
+First the Fujii index makes a high pass filtering,
+this is evident if we look at the maximum values of the curves,
+being greater in the Z (high frequencies) band and rapidly decrease in the Y and X (low frequencies) bands.
+Second, the index undergoes a normalization, in the denominator of the Equation \ref{eq:contFujii2},
+with the intention of reducing the index dependence with the sample level of illumination.
+Not to mention that this normalization, in the case of frequency band analysis, is done with unfiltered signal data.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this work were presented comparisons between the values of the temporal speckle 
+In the ink drying test, 
+we analyze the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
+by the separation of the signals in different frequency bands;
+when there is a process that changes its behavior over time.
+
+In the paper piece test, we consider that no material is completely inert, 
+and consequently, 
+a dynamic speckle analysis will show us how the speckle light intensity variations can be interpret as the sample activity level or as the set default level noise in the test,
+we use the first case,
+the effect in the speckle light intensity occasioned by the laser light intensity variation.
+
+By the analysis shown in the Figures \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
+we can observe that the greater the laser illumination level $\mu_p$, 
+the greater the range of speckle light intensity variation $\sigma_p$ of each pixel analyzed, 
+however this increase depend of speckle signal frequency band analyzed.
+This is reaffirmed by the analysis of the ink drying test, 
+seen in the Figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
+where the curves of regions with high and low luminosity are compared.
+
+Thus, by the results shown in the Figures \ref{fig:numerical} and \ref{fig:papelilllevel},
+we can theorize that this augmentative effect of the dynamic range in the speckle, acts predominantly on speckle signals with low frequency components, and in smaller predominance on speckle signals with high frequency components.
+This hypothesis is supported by other works with similar results \cite{Nothdurft:05},
+where the temporal speckle mean matrix shows information about the surface of sample and the laser illumination level, and the temporal speckle deviation matrix shows information of material inside at different levels and in less proportion the information of the laser illumination level.
+Given that the mean value collect information of zero frequency component in the speckle signal, 
+and the standard deviation  collect information of non-zero frequency components.
+We can make a parallel, with the results obtained in the present work,
+and thus  to indicate that the speckle signals with frequency components with greater value are less affected in their dynamic range by the variation of the laser light intensity.
+By analyzing the index Fujii, we also highlight that generalizations cannot be made for all speckle indices,
+In this work we mainly use the standard deviation, because its calculation is directly linked to the value, or amplitude, root mean square of the signals.
+In counter-parted, the Fujii index makes a previous filtering and a non-linear scaling with respect to the light intensity, which hinders a fair interpretation, of its behavior for different frequency bands.
+
+Thus, in this work were presented comparisons between the values of the temporal speckle 
 deviation index to three different frequency bands of the speckle signal and

### 2019-07-29 mcode-fujii/func_curva_lux.m

@@ -1,0 +1,41 @@
+function [F Fx Fy Fz ] = func_curva_lux(DIRECTORY,PATTERN,NUMIMGI,NUMIMGF,POIN2D)
+    close all
+
+
+    IMAGESDIR=DIRECTORY;
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %close all;
+    DATAT =datapack(IMAGESDIR,PATTERN,NUMIMGI,NUMIMGF,'bmp');
+    F=fujii(DATAT,'off');
+
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    disp('Filtering DATAPACK ...')
+    ORDER=32;
+    a=1/3.0;
+    b=2/3.0;
+    H0=fir1(ORDER,b,'low');
+    [DATAT0 DATATz]=firfilterbank(DATAT,H0,'MODE0');
+    H0=fir1(ORDER,a,'low');
+    [DATATx DATATy]=firfilterbank(DATAT0,H0,'MODE0');
+    clear DATAT0
+    disp('done')
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    Fx=fujii(DATATx,'off');
+
+
+    Fy=fujii(DATATy,'off');
+
+
+    Fz=fujii(DATATz,'off');
+
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+end
+

### 2019-07-29 mcode-fujii/funcs2/histograma_bsi.m

@@ -1,0 +1,64 @@
+function [LUX VAL ERR NN]=histograma_bsi(E1,D1,NSAMPLES,POINT)
+
+
+
+    NLIN=size(E1,1);
+    NCOL=size(E1,2);
+
+    VAL2=cell(1,255);
+
+    MINL=min(POINT(:,1));
+    MINC=min(POINT(:,2));
+
+    MAXL=max(POINT(:,1));
+    MAXC=max(POINT(:,2));
+
+
+    for II=MINL:MAXL
+    for JJ=MINC:MAXC
+        in = inpolygon (II, JJ, POINT(:,1), POINT(:,2));
+        if in
+            ID=round(E1(II,JJ))+1;
+            VAL2{ID}(end+1)=D1(II,JJ);
+        end
+    end
+    fprintf('Working histograma_bsi line %3d of %3d\r',II,MAXL);
+    end
+    disp('');
+
+
+    N=0;
+    nn=zeros(1,255);
+    for II=2:255
+        nn(II)=length(VAL2{II});
+        if nn(II)>=NSAMPLES
+            N=N+1;
+        end
+    end
+
+    if(N==0)
+        disp(['Maximo numero de elementos:' num2str(max(nn)) ] );
+        disp(['Valor de limear:' num2str(NSAMPLES)] );
+        error('Numero de elementos LUX igual a 0')
+    end
+
+    LUX=zeros(1,N);
+    VAL=zeros(1,N);
+    ERR=zeros(1,N);
+    NN =zeros(1,N);
+
+    JJ=1;
+    for II=2:255
+        nn=length(VAL2{II});
+        if nn>=NSAMPLES
+            LUX(JJ)=II-1;
+            NN(JJ)=nn;
+            VAL(JJ)=mean(VAL2{II});
+            ERR(JJ)=std(VAL2{II});
+            JJ=JJ+1;
+        end
+    end
+
+
+
+end

### 2019-07-29 mcode-fujii/funcs2/plot_histograma_bsi.m

@@ -1,0 +1,32 @@
+function [LUX VAL ERR NSAMPLES]=plot_histograma_bsi(E,D,NUMERO,POINT)
+
+[LUX VAL ERR NSAMPLES]=histograma_bsi(E,D,NUMERO,POINT);
+
+
+MIN=min(LUX);
+MAX=max(LUX);
+
+
+gcf();
+
+subplot(3,1,1)
+errorbar(LUX,VAL,ERR), grid 
+xlabel('Intensity')
+xlim([MIN MAX])
+%ylim([0 10])
+ylabel('Std intensity')
+
+subplot(3,1,2)
+plot(LUX,100*ERR./VAL,'-o')
+xlabel('Intensity')
+xlim([MIN MAX])
+ylabel('Percentage Std intensity')
+
+subplot(3,1,3)
+plot(LUX,NSAMPLES)
+xlim([MIN MAX])
+xlabel('Mean intensity')
+ylabel('Number of samples')
+
+
+end

### 2019-07-29 mcode-fujii2/func_curva_lux.m

@@ -1,0 +1,41 @@
+function [F Fx Fy Fz ] = func_curva_lux(DIRECTORY,PATTERN,NUMIMGI,NUMIMGF,POIN2D)
+    close all
+
+
+    IMAGESDIR=DIRECTORY;
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %close all;
+    DATAT =datapack(IMAGESDIR,PATTERN,NUMIMGI,NUMIMGF,'bmp');
+    F=fujii2(DATAT,'off');
+
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    disp('Filtering DATAPACK ...')
+    ORDER=32;
+    a=1/3.0;
+    b=2/3.0;
+    H0=fir1(ORDER,b,'low');
+    [DATAT0 DATATz]=firfilterbank(DATAT,H0,'MODE0');
+    H0=fir1(ORDER,a,'low');
+    [DATATx DATATy]=firfilterbank(DATAT0,H0,'MODE0');
+    clear DATAT0
+    disp('done')
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    Fx=fujii2(DATATx,'off');
+
+
+    Fy=fujii2(DATATy,'off');
+
+
+    Fz=fujii2(DATATz,'off');
+
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+end
+

### 2019-07-29 mcode-fujii2/funcs2/fujii2.m

@@ -1,0 +1,104 @@
+%  Copyright (C) 2015, 2016   Roberto Alves Braga Junior
+%
+%  This file is a part of the Bio Speckle Laser Tool Library (BSLTL) package.
+%
+%  This BSLTL computer package is free software; you can redistribute it
+%  and/or modify it under the terms of the GNU General Public License as
+%  published by the Free Software Foundation; either version 3 of the
+%  License, or (at your option) any later version.
+%
+%  This BSLTL computer package is distributed hoping that it could be
+%  useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, please download it from
+%  <http://www.gnu.org/licenses>.
+
+function [Y] = fujii2(DATA,varargin)
+%
+%  This function implements the Fujii Technique [1]. Use as
+%  input data a 3D matrix created grouping NTIMES intensity matrices I(k)
+%  1<=k<=NTIMES
+%
+%  I(k)=DATA(:,:,k)
+%
+%  $FUJII=\sum\limits_{k=1}^{NTIMES-1} \frac{|I(k)-I(k+1)|}{I(k)+I(k+1)+eps}$
+%
+%  The function is normalized to:
+%
+%  $Y=FUJII \frac{200}{NTIMES-1}$
+%
+%  Where (NTIMES-1) is the number of elements in the sum, 2 is a factor to
+%  to do $(I(k)+I(k+1))/2$, a mean value, and 100 is a percentage factor.
+%  Thus the Y matrix represents the expected percentage value of absolute difference 
+%  $|I(k)-I(k+1)|$ relative to the mean value $(I(k)+I(k+1))/2$ for any two 
+%  consecutive values.
+%
+%  $Y \approx 100*E[\frac{|I(k)-I(k+1)|}{(I(k)+I(k+1))/2}]$
+%
+%  References:
+%  [1] FUJII, H. et al. Evaluation of blood flow by laser speckle image sensing. 
+%      Applied Optics, New York, v. 26, n. 24, p. 5321-5325, 1987.
+%
+%
[…]

### 2019-07-29 mcode-fujii2/prog_multiple.m

@@ -1,0 +1,60 @@
+%
+close all
+pkg load bsltl
+pkg load signal
+
+%addpath(genpath('/media/fernando/FER8G-BTRFS/PROGRAMACION/NONGNU.ORG/BSLTL/BSLTL-PKG/bsltl-pkg/bsltl/inst/mfiles'))
+
+%close all
+addpath('funcs2');
+
+
+
+
+
+%%                                                                                                                                                                                              
+
+PASTA={'0min', '10min', '20min', '30min', '40min', '50min', '60min', '75min', '105min', '120min', '150min' };
+TEMPO=[0 , 10, 20, 30, 40, 50, 60, 75,105,120,150];
+
+
+NN=length(PASTA);
+DIRECTORY= '/media/fernando/Hitachi/Resultados/Novos-dados-argentina/';
+PATTERN  = '%d';
+NUMIMGI=1;
+NUMIMGF=400;
+
+POINT=[[50 10];[300 210]];
+%POINT=[[50 260];[300 460]];
+PRENAME='left-'
+%PRENAME='right-'
+
+MEAN_F =zeros(1,NN);
+MEAN_FX=zeros(1,NN);
+MEAN_FY=zeros(1,NN);
+MEAN_FZ=zeros(1,NN);
+
+for II=1:NN
+    LOCALDIR=fullfile(DIRECTORY,PASTA{II})
+    [F Fx Fy Fz]=func_curva_lux(LOCALDIR,PATTERN,NUMIMGI,NUMIMGF,POINT);
+    MEAN_F (II)=mean(mean(F (POINT(:,1)',POINT(:,2)')));
+    MEAN_FX(II)=mean(mean(Fx(POINT(:,1)',POINT(:,2)')));
+    MEAN_FY(II)=mean(mean(Fy(POINT(:,1)',POINT(:,2)')));
+    MEAN_FZ(II)=mean(mean(Fz(POINT(:,1)',POINT(:,2)')));
+end
+
+close all
+FONTSIZE=20;
+
+
+%mkdir([PRENAME 'prog_multiple'])
+
+DATA.TEMPO  =TEMPO;
+DATA.MEAN_F =MEAN_F;
+DATA.MEAN_FX=MEAN_FX;
+DATA.MEAN_FY=MEAN_FY;
+DATA.MEAN_FZ=MEAN_FZ;
+
+save([PRENAME 'data.dat'],'DATA')
+
+

### 2019-07-29 mcode-fujii3/func_curva_lux.m

@@ -1,0 +1,41 @@
+function [F Fx Fy Fz ] = func_curva_lux(DIRECTORY,PATTERN,NUMIMGI,NUMIMGF,POIN2D)
+    close all
+
+
+    IMAGESDIR=DIRECTORY;
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %close all;
+    DATAT =datapack(IMAGESDIR,PATTERN,NUMIMGI,NUMIMGF,'bmp');
+    F=fujii(DATAT,'off');
+
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    disp('Filtering DATAPACK ...')
+    ORDER=32;
+    a=1/3.0;
+    b=2/3.0;
+    H0=fir1(ORDER,b,'low');
+    [DATAT0 DATATz]=firfilterbank(DATAT,H0,'MODE0');
+    H0=fir1(ORDER,a,'low');
+    [DATATx DATATy]=firfilterbank(DATAT0,H0,'MODE0');
+    clear DATAT0
+    disp('done')
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+    Fx=fujii3(DATATx,DATAT,'off');
+
+
+    Fy=fujii3(DATATy,DATAT,'off');
+
+
+    Fz=fujii3(DATATz,DATAT,'off');
+
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+end
+

### 2019-07-29 mcode-fujii3/funcs2/fujii3.m

@@ -1,0 +1,104 @@
+%  Copyright (C) 2015, 2016   Roberto Alves Braga Junior
+%
+%  This file is a part of the Bio Speckle Laser Tool Library (BSLTL) package.
+%
+%  This BSLTL computer package is free software; you can redistribute it
+%  and/or modify it under the terms of the GNU General Public License as
+%  published by the Free Software Foundation; either version 3 of the
+%  License, or (at your option) any later version.
+%
+%  This BSLTL computer package is distributed hoping that it could be
+%  useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
+%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+%  GNU General Public License for more details.
+%
+%  You should have received a copy of the GNU General Public License
+%  along with this program; if not, please download it from
+%  <http://www.gnu.org/licenses>.
+
+function [Y] = fujii3(DATA,DATAT,varargin)
+%
+%  This function implements the Fujii Technique [1]. Use as
+%  input data a 3D matrix created grouping NTIMES intensity matrices I(k)
+%  1<=k<=NTIMES
+%
+%  I(k)=DATA(:,:,k)
+%
+%  $FUJII=\sum\limits_{k=1}^{NTIMES-1} \frac{|I(k)-I(k+1)|}{I(k)+I(k+1)+eps}$
+%
+%  The function is normalized to:
+%
+%  $Y=FUJII \frac{200}{NTIMES-1}$
+%
+%  Where (NTIMES-1) is the number of elements in the sum, 2 is a factor to
+%  to do $(I(k)+I(k+1))/2$, a mean value, and 100 is a percentage factor.
+%  Thus the Y matrix represents the expected percentage value of absolute difference 
+%  $|I(k)-I(k+1)|$ relative to the mean value $(I(k)+I(k+1))/2$ for any two 
+%  consecutive values.
+%
+%  $Y \approx 100*E[\frac{|I(k)-I(k+1)|}{(I(k)+I(k+1))/2}]$
+%
+%  References:
+%  [1] FUJII, H. et al. Evaluation of blood flow by laser speckle image sensing. 
+%      Applied Optics, New York, v. 26, n. 24, p. 5321-5325, 1987.
+%
+%
[…]

### 2019-07-29 mcode-fujii3/prog_multiple.m

@@ -1,0 +1,60 @@
+%
+close all
+pkg load bsltl
+pkg load signal
+
+%addpath(genpath('/media/fernando/FER8G-BTRFS/PROGRAMACION/NONGNU.ORG/BSLTL/BSLTL-PKG/bsltl-pkg/bsltl/inst/mfiles'))
+
+%close all
+addpath('funcs2');
+
+
+
+
+
+%%                                                                                                                                                                                              
+
+PASTA={'0min', '10min', '20min', '30min', '40min', '50min', '60min', '75min', '105min', '120min', '150min' };
+TEMPO=[0 , 10, 20, 30, 40, 50, 60, 75,105,120,150];
+
+
+NN=length(PASTA);
+DIRECTORY= '/media/fernando/Hitachi/Resultados/Novos-dados-argentina/';
+PATTERN  = '%d';
+NUMIMGI=1;
+NUMIMGF=400;
+
+%POINT=[[50 10];[300 210]];
+POINT=[[50 260];[300 460]];
+%PRENAME='left-'
+PRENAME='right-'
+
+MEAN_F =zeros(1,NN);
+MEAN_FX=zeros(1,NN);
+MEAN_FY=zeros(1,NN);
+MEAN_FZ=zeros(1,NN);
+
+for II=1:NN
+    LOCALDIR=fullfile(DIRECTORY,PASTA{II})
+    [F Fx Fy Fz]=func_curva_lux(LOCALDIR,PATTERN,NUMIMGI,NUMIMGF,POINT);
+    MEAN_F (II)=mean(mean(F (POINT(:,1)',POINT(:,2)')));
+    MEAN_FX(II)=mean(mean(Fx(POINT(:,1)',POINT(:,2)')));
+    MEAN_FY(II)=mean(mean(Fy(POINT(:,1)',POINT(:,2)')));
+    MEAN_FZ(II)=mean(mean(Fz(POINT(:,1)',POINT(:,2)')));
+end
+
+close all
+FONTSIZE=20;
+
+
+%mkdir([PRENAME 'prog_multiple'])
+
+DATA.TEMPO  =TEMPO;
+DATA.MEAN_F =MEAN_F;
+DATA.MEAN_FX=MEAN_FX;
+DATA.MEAN_FY=MEAN_FY;
+DATA.MEAN_FZ=MEAN_FZ;
+
+save([PRENAME 'data.dat'],'DATA')
+
+

### 2019-07-29 mcode-fujii3/prog_multiple_plot.m

@@ -1,0 +1,41 @@
+%
+FONTSIZE=20;
+DATAL=load('left-data.dat');
+DATAR=load('right-data.dat');
+
+DATAL = DATAL.DATA;
+DATAR = DATAR.DATA;
+
+TEMPO=[0 , 10, 20, 30, 40, 50, 60, 75,105,120,150];
+
+figure(1)
+plot(TEMPO,DATAL.MEAN_F,'-o',TEMPO,DATAR.MEAN_F,'-*')
+title('<Fujii_T> in time')
+xlabel('Time in min')
+ylabel('<Fujii_T>')
+legend('HIGH','LOW');
+print(figure(1),'fujii-all.eps','-depsc',['-F:',int2str(FONTSIZE)]);
+
+figure(2)
+plot(TEMPO,DATAL.MEAN_FX,'-o',TEMPO,DATAR.MEAN_FX,'-*')
+title('<Fujii_X> in time: [0 - 0.333]Fs/2')
+xlabel('Time in min')
+ylabel('<Fujii_X>')
+legend('HIGH','LOW');
+print(figure(2),'fujii-bandx.eps','-depsc',['-F:',int2str(FONTSIZE)]);
+
+figure(3)
+plot(TEMPO,DATAL.MEAN_FY,'-o',TEMPO,DATAR.MEAN_FY,'-*')
+title('<Fujii_Y> in time: [0.333 - 0.666]Fs/2')
+xlabel('Time in min')
+ylabel('<Fujii_Y>')
+legend('HIGH','LOW');
+print(figure(3),'fujii-bandy.eps','-depsc',['-F:',int2str(FONTSIZE)]);
+
+figure(4)
+plot(TEMPO,DATAL.MEAN_FZ,'-o',TEMPO,DATAR.MEAN_FZ,'-*')
+title('<Fujii_Z> in time: [0.666 - 1.000]Fs/2')
+xlabel('Time in min')
+ylabel('<Fujii_Z>')
+legend('HIGH','LOW');
+print(figure(4),'fujii-bandz.eps','-depsc',['-F:',int2str(FONTSIZE)]);

### 2019-07-29 article/article_1.tex
casi terminado

@@
 Specifically, 
-will be studied as It is influenced the temporal speckle deviation 
+will be studied as it is influenced the temporal speckle deviation 
 index by the use of 3 different frequency bands of the speckle signal.
-Finally, It is shown as signals with high frequency values
-return values with more illumination level independence.
+Finally, it is shown how signals with high frequency components return values with greater illumination level independence.
 \end{abstract}
@@
 \section{Introduction}
-Dynamic laser speckle is a phenomenon that is used to monitor changes in illuminated samples, and it can be measured by multiple indexes \cite{BSLTLBOOK}.
+Dynamic laser speckle is a phenomenon that is used to monitor changes in laser illuminated samples, and it can be measured by multiple indexes \cite{BSLTLBOOK}.
 The indexes are associated to the level of changes and could be expressed by numerical and or graphical outcomes that can be affected by filtering action during the image processing \cite{RIVERA2017144}.
@@
 the chosen frequency band alters the result of selected index.
-By other side, there is still a limitation to make  speckle analysis in the presence of in-homogeneity of illumination, because
+By other side, there is still a limitation to make speckle analysis in the presence of non homogeneous illumination, because
 the most of biospeckle indexes are influenced in their values
-by the use of a illumination level \cite{REIS2016}.
+by the use of an specific illumination level \cite{REIS2016}.
 The illumination level can vary regarding the profile of the sample, such as an apple \cite{KAZ:12a} or a very irregular surface present in a kefir \cite{kefir}. 
@@
 a red laser was pointed to a layer of ink drying monitored by a digital camera;
-the images are collected receiving two different illumination levels, because of the neutral 
-density lens covering partially the laser beam \cite{REIS2016}.
+the images are collected receiving two different illumination levels, 
+because the neutral density lens partially covers partially the laser beam \cite{REIS2016}.
 The images were placed in data packages and
@@
 The test over a steady state paper has a similar configuration that seen in
-the Fig. \ref{fig:system} with the the absence of 
+the Fig. \ref{fig:system} with the absence of 
 the neutral density lens. 
-The phenomenon observed was the noise associated to the experimental configuration linked to the camera, to the resolution of the images and also the mechanical noise, and it was collected one data package
-sampled with a frequency of $F_s=$ 10 hertz, being 
+The phenomenon observed was the speckle signal  variation associated with  the speckle response of material, 
+the experimental setup of the camera, the resolution of the images and also to the mechanical noise; 
+so that it was collected one data package sampled with a frequency of $F_s=$ 10 hertz, being 
 collected in total $N=129$ images of 640$\times$480 pixels.
@@
 Thus, given that the paper activity test and the ink drying test are independent events, 
-without comparison between them self, your sampling frequencies are different.
+without comparison between them self, your sampling frequencies are different,
+and selected according to the best behavior of the curves, 
+being more appropriate higher sampling frequencies for the ink drying test.
 
@@
 Each data package or sub package ($P_T$) went through of a filter bank with 4 outputs  having each
-one a different type of processing, the first output is trivial because it
+one, a different type of processing, the first output is trivial because it
 lets to pass the information freely, this package is called of $P_T$, whilst the other 3 outcomes
@@
 We designate to each image matrix, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, 
-being $k$ an integer index that indicates that it is in use the $k$-th image $\mathbf{I}$ in the package.
+being $k$ an integer index that indicates that, it is in use the $k$-th image $\mathbf{I}$ in the package.
 Thus, to get
@@
 
-Aditionally, the ``temporal speckle deviation index'' can be defined as $\bar{\sigma}=<\sigma>$, the mean value
+Aditionally, the temporal speckle deviation index can be defined as $\bar{\sigma}=<\sigma>$, the mean value
 of all elements in the matrix $\sigma$, being $<.>$ the mean spatial operator.
@@
 The  Fujii matrix mean value can be defined as $\overline{Fujii}=<Fujii>$, the mean value
-of all elements in the matrix $Fujii$.
+of all elements in the $Fujii$ matrix.
 
-The Fujii matrix method represents the attempt to eliminate 
+The Fujii method represents the attempt to eliminate 
 the dependence on illumination level, in a speckle index.
 For this purpose, the method define the index as the mean value of the  first order high pass FIR filter, 
-$\mathbf{I}_{k}-\mathbf{I}_{k+1}$,
-whose values are corrected using an approximation of the intensity mean value, $\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
+$\mathbf{I}_{k}-\mathbf{I}_{k+1}$, similarly to the  $AVD$ index \cite{avd};
+but in the Fujii method the values are corrected using an approximation of the intensity mean value, $\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
 This calculation aspect is the strong point of the method,
-because the Fujii method assumes that the increase in the speckle 
+because the method assumes that the increase in the speckle 
 light dynamic range ($\mathbf{I}_{k}-\mathbf{I}_{k+1}$) 
 will be linear in proportion with the increase in laser light ($\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$).
-This means that the method already uses high frequency components, of the speckle signal, 
-and discards those of low frequency, in addition  to attempting to correct or normalize the index value;
+This means that the method already uses high frequency components, 
+of the speckle signal, 
+and discards those of low frequency, 
+in addition to attempting to correct or  normalize the index values;
 and it is for these characteristics that it shows an acceptable performance,
@@
 Additionally, it was defined the matrix $Fujii_{\alpha}$, 
-as the filtered version of package $P$ to the frequency band $\alpha$, following the Equation \ref{eq:contFujii3}.
+as the index of the filtered version of package $P$ to the frequency band $\alpha$, following the Equation \ref{eq:contFujii3}.
 \begin{equation}\label{eq:contFujii3}
@@
 
-\subsection{Datapack processing in the test of a ink drying}
+\subsection{Datapack processing in the ink drying test}
 \label{subsec:numprocink}
@@
 \label{subsec:statistical}
-We defined $\sigma_i$ and $\mu_i$
+We define $\sigma_i$ and $\mu_i$
 as the values in the $i-th$ position in the $\sigma$  
@@
 
-\subsection{Datapack processing in the test of a steady state paper}
+\subsection{Datapack processing in the steady state paper test}
 \label{subsec:numprocink}
@@
 
-\subsection{Numerical results o the ink drying test} 
+\subsection{Numerical results in the ink drying test} 
 \label{subsec:numericalink}
 
-The activity level analysis in the  ink drying process has as objective  analyze the behavior of dynamic a speckle index, 
-in the context of a process that change your characteristic in time.
+The activity level analysis in the ink drying process has as objective to analyze the behavior of speckle index in a  dynamic process,
+in the context of a system that change your characteristic in time.
 
@@
 As can be seen, when we analyzed the index over the complete frequency band (Fig. \ref{fig:allink}),
-we had different results to both illuminations levels, being high in the left side of the Figure \ref{fig:regions} and low in the right. This 
+we had different results to both illuminations levels, being high in the left side of the Fig. \ref{fig:regions} and low in the right. This 
 indicates a positive influence of illumination level in the index value.
-By other side, if we observe the Figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink}
-we can see how the index values from different
-illuminations  was similar to the frequency level,
+By other side, if we observe the Figs. \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
+we can see how the index values from different illuminations were similar when compared at the same frequency component,
 being greatest similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
-Thus the similarity is limited by the sampling rate used.
 
 Finally, it is important to highlight that in the ink drying test, the information from the dynamic laser speckle is linked to high frequencies in the beginning of the drying process and  speckle signals with low frequencies at end, being gradual the transition
-until reach the lowest level of signal with only the noise of test.
-In Figure \ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a transition of state with the stabilization of the DLSI.
-Thus, after this point, one has only the inner noise of the system influencing the DLSI.
+until reach the lowest level of signal with only the speckle signal of glass plate.
+In Fig.
+\ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a transition of state with the stabilization of the DLSI.
+Thus, after this point, one has only the glass plate speckle signal influencing the DLSI.
 
@@
 In the Fig. \ref{fig:papelstd} we can see the result of data processing from the steady
- paper under dynamic laser speckle phenomenon considering an homogeneous illumination and using the standard deviation $\sigma$ as a dynamic laser speckle index (DLSI). Fig. \ref{fig:papelall}
-represents the $\sigma_T$ matrix with the complete frequency band, while Fig. \ref{fig:papelstd_stdx}
+ paper under dynamic laser speckle phenomenon, 
+considering an homogeneous behavior of the speckle signal and using the standard deviation $\sigma$ as a dynamic laser speckle index (DLSI). 
+Fig. \ref{fig:papelall} represents the $\sigma_T$ matrix with the complete frequency band, while Fig. \ref{fig:papelstd_stdx}
 represents the $\sigma_X$ matrix with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
@@
 
-In Figure \ref{fig:papelilllevel} we present the relation between an average value of $\sigma_p$,
-in the $\sigma$ matrix, with a value $\mu_p$ (mean value representing the illumination level) of the $\mu$ matrix, 
+In Fig. \ref{fig:papelilllevel} we present the relation between an average value of $\sigma_p$,
+in the $\sigma$ matrix, with a value $\mu_p$ (mean value representing the observable illumination level) of the $\mu$ matrix, 
 in the complete frequency band, the value $\mu_p$
-is related to the illumination level in the surface of the sample \cite{Nothdurft:05}
-and the color or material of sample. Thus, when we choose $\mu_p$  as reference 
+is related to the laser illumination level in the surface of the sample \cite{Nothdurft:05}
+and the color of it. Thus, when we choose $\mu_p$  as reference 
 in a homogeneous sample,  
-in true we choose indirectly the illumination level in the surface.
+in true we choose indirectly the observable illumination level in the surface.
 Therefore, Fig. \ref{fig:papelilllevel} shows the variables $\sigma_p$, $e_p$ and $L_p$ in function
@@
 It is import to note that $e_p$ was plot as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$,
-and $L_p$ is the histogram of the values in temporal speckle mean matrix, 
-given that the mean value is zero to any frequency band without the zero frequency,
+and $L_p$ is the histogram of the values in temporal speckle mean matrix.
+Given that the mean value is zero to any frequency band without the zero frequency,
 in the figures are showed the $L_p$ values of the complete frequency band, 
@@
 
-In Figure \ref{fig:illlevel_all}, we observe the absence of tendency in the DLSI ($\sigma$) with respect to the intensity ($\mu$), i.e.
+In Fig.
+\ref{fig:illlevel_all}, we observe the absence of tendency in the DLSI ($\sigma$) with respect to the intensity ($\mu$), i.e.
 with the increase of the $\mu$ value the standard deviation ($\sigma$) does not increase or decrease.
 However, around that constant there is a spread of $\sigma$ to each value of $\mu$ that creates an uncertainty in the outcome, and expressed by the error $e$. 
-Figure \ref{fig:illlevel_all} represents the outcome from the data without filtering, thus with all frequencies.
-And the data is the noise present in the processes of illumination and image acquiring because the sample is a steady paper without changes in the scatterers of the laser light.
-Nevertheless, when we filter the signal (images in time), we can observe a change in the $\sigma$ with respect to the frequency range, unveiling the dependency of the DLSI to the level of illumination and its relation to the frequency.
-In Figure \ref{fig:illlevel_stdx}, in the inferior third of the frequency band, there is a tendency in the $\sigma$ value with respect to the level of light.
-The DLSI changes its value with respect to the illumination level, where in low illumination level one had highest error, with the $\sigma$ values spread around the mean value, and the error tending to zero when the level of light increased in some areas of the sample.
-The same behavior happened in the middle level of frequency band, and much less in the superior third of the frequency band, meaning that in the highest frequencies one had less influence of the level of light in the $\sigma$ values.
-Since the $\sigma$ DLSI does not filter the signal \cite{RIVERA2017144}, it must be considered this situation during the DLSI usage, as one can compromise the outcome by the influence of the illumination of the sample in the results.
-Dynamic laser speckle indexes can offer other index  options to circumvent that influence, for example, using the Absolute Value of the Differences DLSI and its variations \cite{BSLTLBOOK}.
+Fig. \ref{fig:illlevel_all} represents the outcome from the data without filtering, thus with all frequencies. 
+And the data are the speckle signals present in a material with low activity, because the sample is a steady paper approximately homogeneous over time and space.
+Nevertheless, when we filter the signal (images in time), 
+we can observe a change in the $\sigma$ with respect to the frequency range, 
+unveiling the dependency of the DLSI to the level of illumination and its relation to the frequency.
+In Fig. \ref{fig:illlevel_stdx}, corresponding to the inferior third of the frequency band, 
+there is a tendency in the $\sigma$ value with respect to the level of light. 
+The DLSI changes its value with respect to the illumination level $\mu_p$, 
+where in low illumination level we had highest error, 
+%with the $\sigma$ values spread around the mean value, 
+and the error tending to zero when the level of light ($\mu_p$) increased in some areas of the sample. 
+The same behavior happened in the middle level of frequency band, 
+and much less in the superior third of the frequency band, 
+meaning that in the highest frequencies one had less influence of the level of light ($\mu_p$) in the $\sigma$ values. 
+Since the $\sigma$ DLSI does not filter the signal \cite{RIVERA2017144}, 
+it must be considered this situation during the usage of any DLSI, 
+and of how this one can compromise the outcome by the influence of the illumination of the sample in the results.
+Other dynamic laser speckle indexes may offer other options to avoid this influence,
+for example, using the Absolute Value of the Differences DLSI and its variations \cite{BSLTLBOOK}.
 
-\subsection{Numerical results using Fujii} 
+\subsection{Fujii index in the ink drying test} 
 \label{subsec:vsfujii}
 
-The Figure \ref{fig:fujiiallink} shows the behavior of mean value to the Fujii matrix
+The Fig. \ref{fig:fujiiallink} shows the behavior of mean value to the Fujii matrix
 defined in the Equation \ref{eq:contFujii2}.
-The Figures \ref{fig:fujiixink}, \ref{fig:fujiiyink} and \ref{fig:fujiizink},
+The Figs. \ref{fig:fujiixink}, \ref{fig:fujiiyink} and \ref{fig:fujiizink},
 show the behavior of mean value to the Fujii matrix defined in the Equation \ref{eq:contFujii3},
-to the cases of frequency bands X,Y and Z respectively. 
+to the cases of frequency bands X,Y and Z respectively. In all cases we worked on the ink drying test.
 \begin{figure}[!h]
@@
 
-By the analysis shown in the Figures \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
+By the analysis shown in the Figs. \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
 we can observe that the greater the laser illumination level $\mu_p$, 
@@
 This is reaffirmed by the analysis of the ink drying test, 
-seen in the Figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
+seen in the Figs. \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
 where the curves of regions with high and low luminosity are compared.
 
-Thus, by the results shown in the Figures \ref{fig:numerical} and \ref{fig:papelilllevel},
+Thus, by the results shown in the Figs. \ref{fig:numerical} and \ref{fig:papelilllevel},
 we can theorize that this augmentative effect of the dynamic range in the speckle, acts predominantly on speckle signals with low frequency components, and in smaller predominance on speckle signals with high frequency components.
@@
 and thus  to indicate that the speckle signals with frequency components with greater value are less affected in their dynamic range by the variation of the laser light intensity.
-By analyzing the index Fujii, we also highlight that generalizations cannot be made for all speckle indices,
+By analyzing the index Fujii, we also highlight that generalizations cannot be made for all speckle indices.
 In this work we mainly use the standard deviation, because its calculation is directly linked to the value, or amplitude, root mean square of the signals.
@@
 
-Thus, in this work were presented comparisons between the values of the temporal speckle 
-deviation index to three different frequency bands of the speckle signal and
-different illuminations levels, in a
-dynamic laser speckle analysis. The results showed that the influence of the illumination level in
-the DLSI index, like the temporal speckle deviation 
-index, decreases with the use of signals with high frequency bands.
+Thus, in this work were presented comparisons between the values of the temporal speckle deviation index for three different frequency bands of the speckle signal and different illuminations levels, 
+in a dynamic laser speckle analysis. 
+The results showed that the influence of the illumination level in a DLSI, 
+like the temporal speckle deviation index, 
+decreases with the use of signals with high frequency components.
 

### 2019-08-02 article/article_1.tex
revisado

@@
 
-\title{Analysis of Illumination Dependency  in the Dynamic Laser Speckle Analysis}
+\title{Study of Illumination Dependency  in the Dynamic Laser Speckle Analysis}
 %\tnotetext[mytitlenote]{Fully documented templates are available in the 
@@
 \begin{abstract}
-In this article we show an analysis of how the frequency band,
-of the speckle signal, influence in the
-light independence of the speckle index value in a dynamic laser speckle analysis. 
+In this article we show an analysis of how the frequency bands 
+influence in the light independence of the speckle index value in a dynamic laser speckle analysis. 
 Specifically, 
-will be studied as it is influenced the temporal speckle deviation 
-index by the use of 3 different frequency bands of the speckle signal.
-Finally, it is shown how signals with high frequency components return values with greater illumination level independence.
+we studied temporal speckle deviation 
+index influenced by the use of three different frequency bands of the speckle signal. 
+Finally, it was shown how signals with high frequency components return values with greater illumination level independence.
 \end{abstract}
@@
 In the ink drying test, 
-we analyze the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
+we analyzed the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
 by the separation of the signals in different frequency bands;
-when there is a process that changes its behavior over time.
+when there was a process that changes its behavior over time.
 
-In the paper piece test, we consider that no material is completely inert, 
+In the paper piece test, we considered that no material is completely inert, 
 and consequently, 

### 2019-08-05 article/article_1.tex
corrigindo pontos a resaltar

@@
 
-In the paper piece test, we considered that no material is completely inert, 
-and consequently, 
-a dynamic speckle analysis will show us how the speckle light intensity variations can be interpret as the sample activity level or as the set default level noise in the test,
-we use the first case,
-the effect in the speckle light intensity occasioned by the laser light intensity variation.
+In the paper piece test, we considered that none material is completely inert and, consequently, 
+the observed signal  in the  dynamic speckle analysis has more than noise.
 

### 2020-01-23 article/article_1.tex
revision de contnido antes de revisar ingles

@@
 \includegraphics[width=0.65\columnwidth]{system.eps}
-\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of ink drying.}
+\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system 
+with the levels of illumination over a layer of ink drying.}
 \label{fig:system}
@@
 \includegraphics[width=0.85\columnwidth]{meanall.eps}
-\caption{Light intensity distribution in the paper piece test with highest illumination presented by red pixels and lowest by blue pixels.}
+\caption{Light intensity distribution in the paper piece test with highest illumination 
+presented by red pixels and lowest by blue pixels.}
 \label{fig:meanpaper}
@@
 $\mathbf{I}_{k}-\mathbf{I}_{k+1}$, similarly to the  $AVD$ index \cite{avd};
-but in the Fujii method the values are corrected using an approximation of the intensity mean value, $\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
+but in the Fujii method the values are corrected using an approximation of the intensity mean value, 
+$\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
 This calculation aspect is the strong point of the method,
@@
 
-In this test we have one data package that was filtered (\ref{fig:filtering2}) obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
+In this test we have one data package that was filtered (\ref{fig:filtering2}) 
+obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
 temporal speckle deviation matrix, as can be seen in the Fig. \ref{fig:filtering2}.
@@
 
-The activity level analysis in the ink drying process has as objective to analyze the behavior of speckle index in a  dynamic process,
+The activity level analysis in the ink drying process has as objective to analyze 
+the behavior of speckle index in a  dynamic process,
 in the context of a system that change your characteristic in time.
@@
 In the Fig. \ref{fig:numerical}, we can see the result of processing 
- the ink drying test under the dynamic laser speckle index (DLSI) in two areas with different level of illumination. The Fig. \ref{fig:allink}
+ the ink drying test under the dynamic laser speckle index (DLSI) in two areas with 
+different level of illumination. The Fig. \ref{fig:allink}
 represents the $\bar{\sigma}_T$ value in two light intensity levels, and it is done using the package $P_T$
@@
 As can be seen, when we analyzed the index over the complete frequency band (Fig. \ref{fig:allink}),
-we had different results to both illuminations levels, being high in the left side of the Fig. \ref{fig:regions} and low in the right. This 
+we had different results to both illuminations levels, being high in the left 
+side of the Fig. \ref{fig:regions} and low in the right. This 
 indicates a positive influence of illumination level in the index value.
@@
 
-Finally, it is important to highlight that in the ink drying test, the information from the dynamic laser speckle is linked to high frequencies in the beginning of the drying process and  speckle signals with low frequencies at end, being gradual the transition
+Finally, it is important to highlight that in the ink drying test, the information 
+from the dynamic laser speckle is linked to high frequencies in the beginning of 
+the drying process and  speckle signals with low frequencies at end, being gradual the transition
 until reach the lowest level of signal with only the speckle signal of glass plate.
-In Fig.
-\ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a transition of state with the stabilization of the DLSI.
-Thus, after this point, one has only the glass plate speckle signal influencing the DLSI.
+In Fig. \ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a 
+transition of state with the stabilization of the DLSI. Thus, after this point, 
+one has only the glass plate speckle signal influencing the DLSI.
 
@@
 
-%The paper piece test has a quasi-circular laser light distribution around a center and with decreasing light intensity with increasing the radius.
+%The paper piece test has a quasi-circular laser light distribution around a center and with decreasing 
+light intensity with increasing the radius.
 
@@
  paper under dynamic laser speckle phenomenon, 
-considering an homogeneous behavior of the speckle signal and using the standard deviation $\sigma$ as a dynamic laser speckle index (DLSI). 
+considering an homogeneous behavior of the speckle signal and using the standard deviation $\sigma$ 
+as a dynamic laser speckle index (DLSI). 
 Fig. \ref{fig:papelall} represents the $\sigma_T$ matrix with the complete frequency band, while Fig. \ref{fig:papelstd_stdx}
 represents the $\sigma_X$ matrix with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
-Fig. \ref{fig:papelstd_stdy} represents the $\sigma_Y$ matrix with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz, and Fig. \ref{fig:papelstd_stdz} 
+Fig. \ref{fig:papelstd_stdy} represents the $\sigma_Y$ matrix with the frequency band between 
+$\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz, and Fig. \ref{fig:papelstd_stdz} 
 represents the $\sigma_Z$ matrix with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
@@
 Therefore, Fig. \ref{fig:papelilllevel} shows the variables $\sigma_p$, $e_p$ and $L_p$ in function
-of  $\mu_p$, to the case of the complete frequency band (\ref{fig:illlevel_all}), the inferior third of the frequency band (\ref{fig:illlevel_stdx}),
-the middle third of the frequency band (\ref{fig:illlevel_stdy}) and the superior third of the frequency band (\ref{fig:illlevel_stdz}).
+of  $\mu_p$, to the case of the complete frequency band (\ref{fig:illlevel_all}), 
+the inferior third of the frequency band (\ref{fig:illlevel_stdx}),
+the middle third of the frequency band (\ref{fig:illlevel_stdy}) 
+and the superior third of the frequency band (\ref{fig:illlevel_stdz}). 
 It is import to note that $e_p$ was plot as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$,
@@
 
-In Fig.
-\ref{fig:illlevel_all}, we observe the absence of tendency in the DLSI ($\sigma$) with respect to the intensity ($\mu$), i.e.
-with the increase of the $\mu$ value the standard deviation ($\sigma$) does not increase or decrease.
-However, around that constant there is a spread of $\sigma$ to each value of $\mu$ that creates an uncertainty in the outcome, and expressed by the error $e$. 
+In Fig. \ref{fig:illlevel_all}, we observe the absence of tendency in the DLSI ($\sigma$) 
+with respect to the intensity ($\mu$), 
+i.e. with the increase of the $\mu$ value the standard deviation ($\sigma$) does not increase or decrease. 
+However, around that constant there is a spread of $\sigma$ to each value of $\mu$ that creates an uncertainty in the outcome, 
+and expressed by the error $e$. 
 Fig. \ref{fig:illlevel_all} represents the outcome from the data without filtering, thus with all frequencies. 
-And the data are the speckle signals present in a material with low activity, because the sample is a steady paper approximately homogeneous over time and space.
+And the data are the speckle signals present in a material with low activity, 
+because the sample is a steady paper approximately homogeneous over time and space.
 Nevertheless, when we filter the signal (images in time), 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Final comments}
+
+By the results shown in the Figs. \ref{fig:numerical} and \ref{fig:papelilllevel},
+we can theorize that the dynamic range,
+between the samples with greater and  less values, 
+in  the temporal speckle deviation index,
+they are greater on speckle signals with low frequency components, 
+and  smaller on speckle signals with high frequency components;
+thus, we can observe that the effect of illumination level in 
+the variability of the temporal speckle deviation index decrease with the frequency.
+This hypothesis is supported by other works with similar results \cite{Nothdurft:05},
+where the temporal speckle mean matrix shows information about the surface of sample and the laser illumination level, 
+and the temporal speckle deviation matrix shows information of material inside at 
+different levels and in less proportion the information of the laser illumination level.
+Given that the mean value collect information of zero frequency component in the speckle signal, 
+and the standard deviation  collect information of non-zero frequency components.
+We can make a parallel, 
+with the results obtained in the present work,
+and thus  to indicate that the speckle signals with high frequency components
+ are less affected in their dynamic range by the variation of the laser light intensity.
+By analyzing the index Fujii, 
+we also highlight that generalizations cannot be made for all speckle indices.
+In this work we mainly use the standard deviation, because its calculation is directly linked to the value, 
+or amplitude, root mean square of the signals.
+In counter-parted, the Fujii index makes a previous filtering (subtract a sample with the previous one) 
+and a non-linear scaling with respect to the light intensity (divide by the average intensity between two consecutive samples), 
+which hinders a fair interpretation, of its behavior for different frequency bands.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
@@
 In the ink drying test, 
-we analyzed the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
-by the separation of the signals in different frequency bands;
-when there was a process that changes its behavior over time.
-
-In the paper piece test, we considered that none material is completely inert and, consequently, 
+we analyzed a process that changes its behavior over time,
+and we seen the effect produced in  the speckle light intensity, 
+and consequently in the standard deviation index, 
+by the separation of the signals in different frequency bands.
+By other side, in the paper piece test, 
+we considered that none material is completely inert and, consequently, 
 the observed signal  in the  dynamic speckle analysis has more than noise.
 
-By the analysis shown in the Figs. \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
-we can observe that the greater the laser illumination level $\mu_p$, 
-the greater the range of speckle light intensity variation $\sigma_p$ of each pixel analyzed, 
-however this increase depend of speckle signal frequency band analyzed.
+%% Mayor quantidade de luz, mayor sigma index
+By the analysis of paper piece shown in the Figs. \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
+we can see that the greater the observable laser illumination level $\mu_p$, 
+the greater will the $\sigma_p$ index of each pixel analyzed, 
+however this increase depend of frequency band in the speckle signal  analyzed;
+by example, in the Fig. \ref{fig:illlevel_stdz},
+with high frequency components, the relation between $\mu_p$ and $\sigma_p$ its almost a horizontal line, 
+this mean that the variation of $\mu_p$ no affect significantly to the $\sigma_p$ index.
 This is reaffirmed by the analysis of the ink drying test, 
 seen in the Figs. \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
-where the curves of regions with high and low luminosity are compared.
+where the curves of regions with high and low luminosity are compared in different frequency bands,
+being the case with high frequency band  (Fig. \ref{fig:stdzink}) 
+the one that produces very similar indices, despite the difference in the illumination level.
 
-Thus, by the results shown in the Figs. \ref{fig:numerical} and \ref{fig:papelilllevel},
-we can theorize that this augmentative effect of the dynamic range in the speckle, acts predominantly on speckle signals with low frequency components, and in smaller predominance on speckle signals with high frequency components.
-This hypothesis is supported by other works with similar results \cite{Nothdurft:05},
-where the temporal speckle mean matrix shows information about the surface of sample and the laser illumination level, and the temporal speckle deviation matrix shows information of material inside at different levels and in less proportion the information of the laser illumination level.
-Given that the mean value collect information of zero frequency component in the speckle signal, 
-and the standard deviation  collect information of non-zero frequency components.
-We can make a parallel, with the results obtained in the present work,
-and thus  to indicate that the speckle signals with frequency components with greater value are less affected in their dynamic range by the variation of the laser light intensity.
-By analyzing the index Fujii, we also highlight that generalizations cannot be made for all speckle indices.
-In this work we mainly use the standard deviation, because its calculation is directly linked to the value, or amplitude, root mean square of the signals.
-In counter-parted, the Fujii index makes a previous filtering and a non-linear scaling with respect to the light intensity, which hinders a fair interpretation, of its behavior for different frequency bands.
-
-Thus, in this work were presented comparisons between the values of the temporal speckle deviation index for three different frequency bands of the speckle signal and different illuminations levels, 
-in a dynamic laser speckle analysis. 
-The results showed that the influence of the illumination level in a DLSI, 
+Thus, in this work were presented comparisons between the values of the temporal 
+speckle deviation index for three different frequency bands of the speckle signal and 
+different illuminations levels in a dynamic laser speckle analysis. 
+The results showed that the influence of the observable illumination level in a DLSI, 
 like the temporal speckle deviation index, 

### 2020-02-13 article/article_1.tex
unificando o texto

--- 2019-08-05 article/article_1.tex
@@
 \usepackage{url}
-%
 \usepackage[breaklinks]{hyperref}
 \usepackage{breakurl}
-
 \usepackage[ruled]{algorithm2e}
-
-%\usepackage{lineno}
-%\modulolinenumbers[5]
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
-%% Elsevier bibliography styles
-%%%%%%%%%%%%%%%%%%%%%%%
-%% To change the style, put a % in front of the second line of the current style and
-%% remove the % from the second line of the style you would like to use.
-%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{elsarticle-num}
 
-%% Numbered
-%\bibliographystyle{model1-num-names}
-
-%% Numbered without titles
-%\bibliographystyle{model1a-num-names}
-
-%% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
-
-%% Vancouver numbered
-%\usepackage{numcompress}\bibliographystyle{model3-num-names}
-
-%% Vancouver name/year
-%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
-
-%% APA style
-%\bibliographystyle{model5-names}\biboptions{authoryear}
-
-%% AMA style
-%\usepackage{numcompress}\bibliographystyle{model6-num-names}
-
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
-%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{graphicx}
 \usepackage{subcaption}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'
-
+\usepackage[svgnames]{xcolor}
 \usepackage{amsmath}
@@
 \usepackage{amssymb}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Study of Illumination Dependency  in the Dynamic Laser Speckle Analysis}
-%\tnotetext[mytitlenote]{Fully documented templates are available in the 
-%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
+\title{Illumination Dependency in Dynamic Laser Speckle Analysis}
 
-% Group authors per affiliation:
 \author{Fernando Pujaico Rivera}
-\author{Roberto Alves Braga Jr.}
+\author{Roberto Alves Braga, Jr.}
 
-\address{University Federal of Lavras, Lavras, Brazil}
+\address{Federal University of Lavras, Lavras, Brazil}
 \fntext[myfootnote2]{201518201@posgrad.ufla.br}
 \fntext[myfootnote1]{robertobraga@deg.ufla.br }
-%
 
 \begin{abstract}
-In this article we show an analysis of how the frequency bands 
-influence in the light independence of the speckle index value in a dynamic laser speckle analysis. 
+We analyse how the frequency bands 
+influence the independence 
+of speckle index values from the level of illumination
+%of the value speckle index from the level of illumination 
+in a dynamic laser speckle analysis.
 Specifically, 
-we studied temporal speckle deviation 
-index influenced by the use of three different frequency bands of the speckle signal. 
-Finally, it was shown how signals with high frequency components return values with greater illumination level independence.
+we study how the temporal speckle deviation 
+index is influenced by the use of three different frequency bands of the speckle signal.
+Finally, it is shown how signals with high frequency components return values with greater independence of the level of illumination.
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-Dynamic laser speckle is a phenomenon that is used to monitor changes in laser illuminated samples, and it can be measured by multiple indexes \cite{BSLTLBOOK}.
-The indexes are associated to the level of changes and could be expressed by numerical and or graphical outcomes that can be affected by filtering action during the image processing \cite{RIVERA2017144}.
-As an example, we have  the $AVD$ \cite{avd} and
-$IM$ \cite{ARIZAGA1999163} indexes, that filter
-the information present in the history of the speckle images like a first order high pass filter with a cut-off in the middle
+Dynamic laser speckle is a phenomenon that is used to monitor changes in laser illuminated samples.
+It can be measured by several different indices \cite{BSLTLBOOK}.
+These indices are associated to the level of changes and can be expressed by numerical and or graphical outcomes that can be affected by filtering during the image processing \cite{RIVERA2017144}.
+As an example, we have  the AVD \cite{avd} and
+IM \cite{ARIZAGA1999163} indices, that filter
+the information present in the history of the speckle images like a first-order high pass filter with a cut-off in the middle
 of the normalized frequency band.
-For this reason, it is important to analyze how
-the chosen frequency band alters the result of selected index.
-By other side, there is still a limitation to make speckle analysis in the presence of non homogeneous illumination, because
-the most of biospeckle indexes are influenced in their values
-by the use of an specific illumination level \cite{REIS2016}.
-The illumination level can vary regarding the profile of the sample, such as an apple \cite{KAZ:12a} or a very irregular surface present in a kefir \cite{kefir}. 
-It can also vary in accordance with the moisture present in the seed \cite{CARDOSO2011} due to the penetration of the light in the sample, or even when the color of the sample vary such as in the interface of cancer and normal tissues \cite{BCB+:12a}.
-And that is the reason to a continuous search for an adequate index, despite the fact there are many of them present in literature \cite{BSLTLBOOK}, but still without a solution to the independence of light intensity.
-The movement toward the portable equipment \cite{Bra:17}, reinforce the need to search the methods and its relation with the illumination. 
-Thus, the present work aimed to establish a relation between the frequency band used
+For this reason, it is important to analyse how
+the chosen frequency band alters the result of a selected index.
+On the other hand, there is still a limitation in making a speckle analysis in the presence of inhomogeneous illumination, because
+most biospeckle indices are influenced
+by the use of a specific level of illumination \cite{REIS2016}.
+The level of illumination can vary regarding the profile of the sample, such as an apple \cite{KAZ:12a} or the very irregular surface present in a kefir \cite{kefir}.
+It can also vary in accordance with the moisture present in a seed \cite{CARDOSO2011} due to the penetration of the light in the sample, or even when the colour of the sample varies, such as in the interface between cancerous and normal tissues \cite{BCB+:12a}.
+This is the reason why there has been a continual search for an adequate index, despite the fact there are many indices presented in the literature \cite{BSLTLBOOK}, but still without a solution that is independent of the intensity of the illumination.
+The move toward portable equipment \cite{Bra:17} reinforces the need to search for such methods and their relation with the illumination.
+Thus, the present work aims to establish a relation between the frequency band used
 and the speckle index; particularly in the dependence of
-the temporal speckle deviation matrix \cite{Nothdurft:05} with the illumination level.
+the temporal speckle deviation matrix \cite{Nothdurft:05} on the level of illumination.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{System description}
+\section{Description of the system}
 \label{sec:description}
 
-\subsection{Data packages of ink drying}
+\subsection{Data for ink drying test}
 \label{sec:descriptionink}
-Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
-a red laser was pointed to a layer of ink drying monitored by a digital camera;
-the images are collected receiving two different illumination levels, 
-because the neutral density lens partially covers partially the laser beam \cite{REIS2016}.
-The images were placed in data packages and
-are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
-collected $N=400$ images by package. In total were collected $11$ packages 
-(with the two different illumination levels each one) at the minutes 
-$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
+Fig.~\ref{fig:system} shows the system setup of the ink sample test during drying, where
+a red laser was pointed at a layer of ink drying, monitored by a digital camera;
+the images were collected receiving two different illumination levels, 
+because the neutral density lens partially covers the laser beam \cite{REIS2016}.
+The images were turned into data-sets:
+the data was acquired with a sampling rate of $F_s=$ 12.5 hertz, with 
+$N=400$ images collected per data-set. In all, there were collected $11$ data-sets 
+(each one with the two different illumination levels) at minutes 
+$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$, $105$, $120$ and $150$ of the drying process.
 \begin{figure}[ht!]
@@
 \includegraphics[width=0.65\columnwidth]{system.eps}
-\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of ink drying.}
+\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system 
+with the levels of illumination over a layer of ink drying.}
 \label{fig:system}
 \end{figure}
-In each image of the packages were selected two regions, of $250\times200$ pixels, 
-corresponding to the regions with two different illumination levels, 
-as shown with red lines in the Fig. \ref{fig:regions}; thus, 
-in the right side of the Fig. \ref{fig:regions}  we have the
-portion of image that was altered by the neutral density lens.
-Thus, the right side has low illumination, and
+Two $250\times200$-pixel regions were selected from each image of the data-sets, 
+corresponding to regions with two different levels of illumination, 
+as shown with red lines in Fig.~\ref{fig:regions}; thus, 
+in the right side of Fig.~\ref{fig:regions}  we have the
+portion of image that was altered by the neutral density lens,
+ so that this side has low illumination, and
 the left side has a high illumination.
@@
 \end{figure}
-%\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\
 
-\subsection{Data packages of a steady state paper}
+\subsection{Data for steady state paper test}
 \label{sec:descriptionpaper}
-The test over a steady state paper has a similar configuration that seen in
-the Fig. \ref{fig:system} with the absence of 
+The test over steady state paper has a similar configuration, as seen in
+Fig.~\ref{fig:system} with the absence of 
 the neutral density lens.
-The phenomenon observed was the speckle signal  variation associated with  the speckle response of material, 
+The phenomenon observed was the variation of the speckle signal associated with  the speckle response of the material, 
 the experimental setup of the camera, the resolution of the images and also to the mechanical noise; 
-so that it was collected one data package sampled with a frequency of $F_s=$ 10 hertz, being 
-collected in total $N=129$ images of 640$\times$480 pixels.
-The Fig. \ref{fig:meanpaper} represents
-with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
-showed in the Sec. \ref{subsec:deviation}; thus, it is easy to see how the
-illumination level of laser over the paper has an elliptical form being highest 
+so that one data-set was collected sampled with a frequency of $F_s=$ 10 hertz. 
+In all, there were $N=129$ 640$\times$480-pixel images collected.
+Fig.~\ref{fig:meanpaper} represents
+with a colour bar the result of calculating the temporal speckle mean matrix ($\mu$) using Eq.~(\ref{eq:cont1})
+of Section~\ref{subsec:deviation}; thus, it is easy to see how the
+laser illumination in piece of paper
+%level of illumination by the laser of the paper 
+has an elliptical form, being highest 
 close to the top of the image.
@@
 \includegraphics[width=0.85\columnwidth]{meanall.eps}
-\caption{Light intensity distribution in the paper piece test with highest illumination presented by red pixels and lowest by blue pixels.}
+\caption{Light intensity distribution in the paper test piece with highest illumination 
+presented by red pixels and lowest by blue pixels.}
 \label{fig:meanpaper}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Numerical analysis}
@@
 
-The sampling frequency used in the analysis of each test, 
-it was selected  trying to achieve the best speed of sampling to observe each phenomenon. 
-The purpose of these two tests is to observe the behavior of the indices in two cases; 
-one with an activity homogeneous level in space and time, and another with a heterogeneous activity.
+The sampling frequency used in the analysis of each test 
+was selected so as to achieve the best speed of sampling to observe 
+an appropriate frequency band of each phenomenon.
+The purpose of these two tests is to observe the behaviour of the indices in two cases: 
+one with an homogeneous activity level in space and time, and another with a heterogeneous activity level.
 Thus, given that the paper activity test and the ink drying test are independent events, 
-without comparison between them self, your sampling frequencies are different,
-and selected according to the best behavior of the curves, 
-being more appropriate higher sampling frequencies for the ink drying test.
+without comparison between them, their sampling frequencies are different,
+and selected according to the best behaviour of the curves, 
+higher sampling frequencies being more appropriate for the ink drying test.
 
-\subsection{Data package filtering in three frequency band}
+\subsection{Data filtering in three frequency bands}
 \label{subsec:firfilters}
-Each data package or sub package ($P_T$) went through of a filter bank with 4 outputs  having each
-one, a different type of processing, the first output is trivial because it
-lets to pass the information freely, this package is called of $P_T$, whilst the other 3 outcomes
-return  signals filtered by a frequency band; thus, 
-we have the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
+Each data-set or sub-set ($P_T$) went through a filter bank with 4 outputs. Each
+one had a different type of processing. The first one was trivial: 
+the data was passed through without change. This data-set is referred to as $P_T$. The other three outcomes
+return  signals filtered in different frequency bands: 
+the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
 the band between $[\frac{1}{3},\frac{2}{3}]\frac{F_s}{2}$ (intermediate frequencies) and
-the band between $[\frac{2}{3},1]\frac{F_s}{2}$ (high frequencies); obtaining at end, the packages 
-$P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in the  Fig. \ref{fig:firfilters}.
-The filtered packages of images were carried out using cascades
-of two low-pass Finite Impulse Response ($FIR$) filters of order $32$, so that
-the sum of signals $P_X+P_Y+P_Z=P_T$.
+the band between $[\frac{2}{3},1]\frac{F_s}{2}$ (high frequencies). This ultimately yields the data-sets 
+$P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in Fig.~\ref{fig:firfilters}.
+The filtered data of the images were made using cascades
+of two low-pass Finite Impulse Response (FIR) filters of order $32$, so that
+$P_X+P_Y+P_Z=P_T$.
 \begin{figure}[h!]
@@
 \includegraphics[width=0.55\columnwidth]{firfilters.eps}
-\caption{Filtering of data packages.}
+\caption{Filtering the data-sets.}
 \label{fig:firfilters}
@@
 The temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05},
-used to compare the results, it was obtained from the $N$ images of the data package $P$.
-We designate to each image matrix, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, 
-being $k$ an integer index that indicates that, it is in use the $k$-th image $\mathbf{I}$ in the package.
-Thus, to get
-% the value $\bar{\sigma}$, it is necessary to get 
-the matrix $\sigma$ is used the Equation \ref{eq:cont2}, 
+used to compare the results, was obtained from the $N$ images of the data-set $P$.
+We designate each image matrix in $P$ as $\mathbf{I}_{k}$, $1\leq k \leq N$, 
+with $k$ an integer that indicates whether the $k$-th image $\mathbf{I}_{k}$ in the data-set was used.
+Thus, the following equation was used to get
+the matrix $\sigma$:
 \begin{equation}\label{eq:cont2}
@@
 \end{equation}
-being that, the matrix $\mu$ can be calculated as, 
+so that the matrix $\mu$ can be calculated as
 \begin{equation}\label{eq:cont1}
@@
 In these last two equations, all the operations are matricial, 
-so that each element (aka pixel) $\mathbf{I}_{k}(i)$ in the matrix $\mathbf{I}_{k}$
-should be processed with your  counterpart $\mathbf{I}_{k+1}(i)$ in the matrix $\mathbf{I}_{k+1}$.
+so that each element (i.e.\ pixel) $\mathbf{I}_{k}(i)$ in the matrix $\mathbf{I}_{k}$
+should be processed with its  counterpart $\mathbf{I}_{k+1}(i)$ in the matrix $\mathbf{I}_{k+1}$.
 
 Aditionally, the temporal speckle deviation index can be defined as $\bar{\sigma}=<\sigma>$, the mean value
-of all elements in the matrix $\sigma$, being $<.>$ the mean spatial operator.
-%And $\sigma_p$ as any value of an element in  $\sigma$.
+of all elements in the matrix $\sigma$, with $<.>$ being the mean spatial operator.
 
@@
 
-The Fujii matrix \cite{Fujii:87} is obtained from the $N$ images in the data package $P$.
-Similarly to the Section \ref{subsec:deviation}, 
-we designate to each image matrix, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$.
-Thus, to get the Fujii matrix is used the Equation \ref{eq:contFujii2}, 
+The Fujii matrix \cite{Fujii:87} is obtained from the $N$ images in $P$.
+Similarly to Section~\ref{subsec:deviation}, 
+we designate each image matrix in $P$ as $\mathbf{I}_{k}$, $1\leq k \leq N$.
+Thus, the following equation is used to get the Fujii matrix:
 \begin{equation}\label{eq:contFujii2}
@@
 \end{equation} 
-The  Fujii matrix mean value can be defined as $\overline{Fujii}=<Fujii>$, the mean value
+The mean value of the Fujii matrix can be defined as $\overline{Fujii}=<Fujii>$, the mean value
 of all elements in the $Fujii$ matrix.
 
-The Fujii method represents the attempt to eliminate 
-the dependence on illumination level, in a speckle index.
-For this purpose, the method define the index as the mean value of the  first order high pass FIR filter, 
-$\mathbf{I}_{k}-\mathbf{I}_{k+1}$, similarly to the  $AVD$ index \cite{avd};
-but in the Fujii method the values are corrected using an approximation of the intensity mean value, $\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
-This calculation aspect is the strong point of the method,
-because the method assumes that the increase in the speckle 
-light dynamic range ($\mathbf{I}_{k}-\mathbf{I}_{k+1}$) 
-will be linear in proportion with the increase in laser light ($\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$).
-This means that the method already uses high frequency components, 
+The Fujii method is an attempt to eliminate 
+the dependence of a speckle index on the level 
+of illumination. For this purpose, the method defines the index as the mean value of the  first-order high pass FIR filter 
+$\mathbf{I}_{k}-\mathbf{I}_{k+1}$, similarly to the  AVD index \cite{avd};
+but in the Fujii method the values are corrected using an approximation of the mean value of the intensity, 
+$\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$.
+This aspect of the calculation is the strong point of the method,
+because the method assumes that the increase in the dynamic range of the speckle 
+light ($\mathbf{I}_{k}-\mathbf{I}_{k+1}$) 
+will be linear in proportion with the increase in the laser light ($\frac{\mathbf{I}_{k}+\mathbf{I}_{k+1}}{2}$).
+This means that the method already uses the high frequency components
 of the speckle signal, 
 and discards those of low frequency, 
-in addition to attempting to correct or  normalize the index values;
-and it is for these characteristics that it shows an acceptable performance,
-to eliminate or decrease the dependence of the index with the laser intensity level.
+in addition to attempting to correct or  normalize the values of the index.
+It is for these reasons that it has an acceptable performance in
+eliminating or decreasing the dependence of the index on the level of intensity of the laser light.
 
-Additionally, it was defined the matrix $Fujii_{\alpha}$, 
-as the index of the filtered version of package $P$ to the frequency band $\alpha$, following the Equation \ref{eq:contFujii3}.
+Additionally, there is defined the matrix $Fujii_{\alpha}$, 
+as the index of the filtered version of $P$ in the frequency band $\alpha$,  using the following equation:
 \begin{equation}\label{eq:contFujii3}
@@
 \end{equation}
-It is important to highlight that the numerator of the last equation, 
-use the signal in the matrices $\mathbf{(I_{\alpha})}_{k}$, that are filtered versions in the frequency band $\alpha$,
+It is important to stress that the numerator of this equation 
+uses the signal in the matrices $\mathbf{(I_{\alpha})}_{k}$, which are filtered versions in the frequency band $\alpha$,
 of the matrix $\mathbf{I}_{k}$.
-By other side, the denominator use the signal $\mathbf{I}_{k}$ which has the complete frequency band.
-This modification was implemented because the numerator, in the calculus, 
-represents or try be the mean value of speckle light intensity, 
-and it value tend to zero in frequency bands without 0 hertz components.
+On the ohter hand, the denominator uses the signal $\mathbf{I}_{k}$, which employs the complete frequency band.
+This modification was implemented because the numerator, in the calculation, 
+represents or tries be the mean value of the intensity of the speckle light, 
+and its value tends to zero in frequency bands without 0 hertz components.
 
-\subsection{Datapack processing in the ink drying test}
+\subsection{Data processing in the ink drying test}
 \label{subsec:numprocink}
 
-We have in the ink drying regions
-two levels of illumination; thus, we  separated each package in two sub package
-(high and low illumination), representing each one of the regions shown in the Fig. \ref{fig:regions}.
-These sub-packages were filtered,
-obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, that was used to obtain
+There are two levels of illumination in the ink drying regions.
+For this reason, we  separated each data-set into two sub-sets
+(high and low illumination), representing each one of the regions shown in Fig.~\ref{fig:regions}.
+These sub-sets were filtered,
+obtaining $P_T$, $P_X$, $P_Y$ and $P_Z$, which were used to obtain
 \begin{figure}[h!]
@@
 \includegraphics[width=0.65\columnwidth]{filtering.eps}
-\caption{Filtering of data packages.}
+\caption{Filtering of data-sets.}
 \label{fig:filtering}
@@
 the temporal speckle deviation matrix and the 
-temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
+temporal speckle deviation indices $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
 $\bar{\sigma}_Z$.
@@
 We define $\sigma_i$ and $\mu_i$
-as the values in the $i-th$ position in the $\sigma$  
-and $\mu$ matrices, respectively; we also defined $\mu_p$
-as any element value in  $\mu$.
-And we define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
-as the set of all $\sigma_i$  values given that $\mu_i\equiv\mu_p$.
-Then, we obtained the vectors $L_p$, $\sigma_p$ and
-$e_p$ using all the $\mu_p$ values, according to:
+as the values in the $i$th position in $\sigma$  
+and $\mu$, respectively. We also define $\mu_p$
+as the value of any element of $\mu$.
+We also define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
+as the set of all values of $\sigma_i$  given that $\mu_i\equiv\mu_p$.
+We thus obtain the vectors $L_p$, $\sigma_p$ and
+$e_p$ using all the values $\mu_p$:
 \begin{itemize}
- \item $L_p(\mu_p)=card\left(S_{\mu_p}\right)$,  being $L_p(\mu_p)$ the number of elements
- in the set $S_{\mu_p}$ and $card(.)$ the cardinality function operator.
- \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, being $\sigma_p(\mu_p)$
- the mean value of elements in the set $S_{\mu_p}$ with $mean(.)$ representing the mean value function operator.
- \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, being $\e_p(\mu_p)$
- the standard  deviation value of elements in the set $S_{\mu_p}$ with $std(.)$ representing the standard deviation function operator.
+ \item $L_p(\mu_p)=card\left(S_{\mu_p}\right)$,  where $L_p(\mu_p)$ is the number of elements
+ in the set $S_{\mu_p}$ and $card(.)$ means the cardinality of a set.
+ \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, where $\sigma_p(\mu_p)$
+ is the mean of the elements in the set $S_{\mu_p}$, with $mean(.)$ denoting the mean value operator.
+ \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, where $e_p(\mu_p)$
+ is the standard  deviation of the elements in the set $S_{\mu_p}$, with $std(.)$ denoting `standard deviation'.
 \end{itemize}
-In practice only will be taken the vectors, values of $\mu_p$
-with a $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.
+In practice, the vectors will only be taken using the values of $\mu_p$
+with $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.
 
-\subsection{Datapack processing in the steady state paper test}
+\subsection{Data processing in the steady state paper test}
 \label{subsec:numprocink}
 
-In this test we have one data package that was filtered (\ref{fig:filtering2}) obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
-temporal speckle deviation matrix, as can be seen in the Fig. \ref{fig:filtering2}.
+In this test we have one data-set that was filtered (\ref{fig:filtering2}) 
+obtaining $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
+temporal speckle deviation matrix, as can be seen in Fig.~\ref{fig:filtering2}.
 
@@
 \includegraphics[width=0.65\columnwidth]{filtering2.eps}
-\caption{Filtering of data package in the steady paper obtaining the mean and the deviation outcomes.}
+\caption{Filtering of the steady paper data-set, obtaining the mean and the deviation.}
 \label{fig:filtering2}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Numerical results} 
@@
 
-In the analysis, the minimum grayscale value, 
-it is fixed by the observable minimum light by the camera or the minimum speckle light intensity in the material analyzed.
-By other side, the maximum grayscale value, 
-it is fixed by the observable maximum light by the camera or the maximum speckle light intensity in the material analyzed.
+In the analysis, the minimum greyscale value 
+is fixed by the minimum light observable by the camera or the minimum speckle light intensity in the material analysed.
+The maximum greyscale value
+is fixed by the maximum light observable by the camera or the maximum speckle light intensity in the material analysed.
 
@@
 
-The activity level analysis in the ink drying process has as objective to analyze the behavior of speckle index in a  dynamic process,
-in the context of a system that change your characteristic in time.
+The activity level analysis in the ink drying process has as objective to analyse 
+the behaviour of the speckle index in a  dynamic process,
+in the context of a system that changes its characteristics over time.
 
-In the Fig. \ref{fig:numerical}, we can see the result of processing 
- the ink drying test under the dynamic laser speckle index (DLSI) in two areas with different level of illumination. The Fig. \ref{fig:allink}
-represents the $\bar{\sigma}_T$ value in two light intensity levels, and it is done using the package $P_T$
-trough the time, with the complete frequency bands.
-The Fig. \ref{fig:stdxink}
-represents the $\bar{\sigma}_X$ value in two light intensity levels, an it is done using the package $P_X$
-trough the time, with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
-The Fig. \ref{fig:stdyink}
-represents the $\bar{\sigma}_Y$ value in two light intensity levels, and it is done using the package $P_Y$
-trough the time, with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
-And the Fig. \ref{fig:stdzink}
-represent the $\bar{\sigma}_Z$ value in two light intensity levels, and it is done using the package $P_Z$
-trough the time, with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
+In Fig.~\ref{fig:numerical}, we can see the result of processing 
+ the data for the ink drying test under the dynamic laser speckle index (DLSI) in two areas with 
+different level of illumination. Fig.~\ref{fig:allink}
+represents $\bar{\sigma}_T$ for two light intensity levels. It was obtained using $P_T$
+over time, with the complete frequency bands.
+Fig.~\ref{fig:stdxink}
+represents $\bar{\sigma}_X$ for two light intensity levels, using $P_X$
+over time, with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$\ Hz.
+Fig.~\ref{fig:stdyink}
+represents $\bar{\sigma}_Y$ for two light intensity levels, using $P_Y$
+over time, with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
+Fig.~\ref{fig:stdzink}
+represents $\bar{\sigma}_Z$ for two light intensity levels, using $P_Z$
+over time, with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
 \begin{figure}[h!]
@@
         \includegraphics[width=\textwidth]{std-all.eps}
-	\caption{$\bar{\sigma}_T$ value through  the time.}
+	\caption{$\bar{\sigma}_T$ over time.}
         \label{fig:allink}
@@
         \includegraphics[width=\textwidth]{std-bandx.eps}
-	\caption{$\bar{\sigma}_X$ value through  the time.}
+	\caption{$\bar{\sigma}_X$ over time.}
         \label{fig:stdxink}
@@
         \includegraphics[width=\textwidth]{std-bandy.eps}
-	\caption{$\bar{\sigma}_Y$ value through  the time.}
+	\caption{$\bar{\sigma}_Y$ over time.}
         \label{fig:stdyink}
@@
         \includegraphics[width=\textwidth]{std-bandz.eps}
-	\caption{$\bar{\sigma}_Z$ value through  the time.}
+	\caption{$\bar{\sigma}_Z$ over time.}
         \label{fig:stdzink}
@@
 
-\caption{Numerical results in the ink drying test.}\label{fig:numerical}
+\caption{Numerical results for the ink drying test.}\label{fig:numerical}
 \end{figure}
 
-As can be seen, when we analyzed the index over the complete frequency band (Fig. \ref{fig:allink}),
-we had different results to both illuminations levels, being high in the left side of the Fig. \ref{fig:regions} and low in the right. This 
-indicates a positive influence of illumination level in the index value.
-By other side, if we observe the Figs. \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
-we can see how the index values from different illuminations were similar when compared at the same frequency component,
-being greatest similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
+As can be seen, when we analysed the index over the complete frequency band (Fig.~\ref{fig:allink}),
+the two different levels of illumination provided different results, high on the left 
+side of Fig.~\ref{fig:regions} and low on the right. This 
+indicates a positive influence of the level of illumination on the index.
+On the other hand, %Figs~\ref{fig:stdxink}, 
+\ref{fig:stdyink} and \ref{fig:stdzink}
+show how the index under different levels of illumination are similar when compared at the same frequency component,
+with the greatest similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
 
-Finally, it is important to highlight that in the ink drying test, the information from the dynamic laser speckle is linked to high frequencies in the beginning of the drying process and  speckle signals with low frequencies at end, being gradual the transition
-until reach the lowest level of signal with only the speckle signal of glass plate.
-In Fig.
-\ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a transition of state with the stabilization of the DLSI.
-Thus, after this point, one has only the glass plate speckle signal influencing the DLSI.
+It is important to stress that in the ink drying test, the information 
+from the dynamic laser speckle is linked to the high frequencies in the beginning of 
+the drying process but with speckle signals with low frequencies at the end, with a gradual transition
+until reaching the lowest 
+level of the signal in the ink drying test, leaving
+%level of the signal, with 
+only the speckle signal of the glass plate.
+In Fig.~\ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a 
+transition of state with the stabilization of the DLSI. Thus, after this point, 
+one has only the glass plate speckle signal influencing the DLSI.
 
-This indicates that the comparisons of index illumination independence
-only should be made between the first minutes because out this range we will be using high contribution of 
-the noise as outcome.
+This indicates that the comparisons of the dependence of the index on the level of illumination
+should only be made during the first few minutes because after that, we will be using the high contribution of 
+the unwanted signals (noise) as the outcome.
 
-\subsection{Numerical results of a steady paper under laser light} 
+\subsection{Numerical results of steady paper under laser light} 
 \label{subsec:numericalpaper}
 
-%The paper piece test has a quasi-circular laser light distribution around a center and with decreasing light intensity with increasing the radius.
+%light intensity with increasing the radius.
 
-Even if the activity level of a paper piece, 
-it  is considered as noise in the context of other tests, where takes place over it, 
-a process of greater activity and variant in time and space. 
-The speckle signal analysis of a paper piece, 
-that for this test we consider approximately homogeneous in its characteristics over time and space,
-will show us  the variation effect of an unique parameter, the light intensity on the dynamic speckle analysis.
+Even though the activity level of a piece of paper 
+is considered as noise in the context of other tests, which are taking place over it, 
+with
+%and although it is 
+a process of greater activity with variations in time and space;
+for the speckle signal analysis of a piece of paper 
+we consider it to be approximately homogeneous in its characteristics over time and space,
+so as to determine the effect on the dynamic speckle analysis of varying only one parameter, the intensity of the illumination.
 
-In the Fig. \ref{fig:papelstd} we can see the result of data processing from the steady
- paper under dynamic laser speckle phenomenon, 
-considering an homogeneous behavior of the speckle signal and using the standard deviation $\sigma$ as a dynamic laser speckle index (DLSI). 
-Fig. \ref{fig:papelall} represents the $\sigma_T$ matrix with the complete frequency band, while Fig. \ref{fig:papelstd_stdx}
-represents the $\sigma_X$ matrix with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
-Fig. \ref{fig:papelstd_stdy} represents the $\sigma_Y$ matrix with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz, and Fig. \ref{fig:papelstd_stdz} 
+Fig.~\ref{fig:papelstd} presents the result of processing the data of the dynamic laser speckle phenomenon gathered from a steady
+ piece of paper,
+considering the homogeneous behaviour of the speckle signal and using the standard deviation $\sigma$ 
+as a dynamic laser speckle index (DLSI).
+Fig.~\ref{fig:papelall} represents the $\sigma_T$ matrix with the complete frequency band, while Fig.~\ref{fig:papelstd_stdx}
+represents the $\sigma_X$ matrix with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$\ Hz.
+Fig.~\ref{fig:papelstd_stdy} represents the $\sigma_Y$ matrix with the frequency band between 
+$\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz, and Fig.~\ref{fig:papelstd_stdz} 
 represents the $\sigma_Z$ matrix with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
@@
         \includegraphics[width=\textwidth]{stdx.eps}
-	\caption{$\sigma_X$ matrix over the inferior third of the frequency band.}
+	\caption{$\sigma_X$ matrix over the lower third of the frequency band.}
         \label{fig:papelstd_stdx}
@@
         \includegraphics[width=\textwidth]{stdz.eps}
-	\caption{$\sigma_Z$ matrix over the superior third of the frequency band.}
+	\caption{$\sigma_Z$ matrix over the upper third of the frequency band.}
         \label{fig:papelstd_stdz}
@@
 
-    \caption{Temporal speckle deviation matrix of paper piece.}
+    \caption{Temporal speckle deviation matrix of a piece of paper.}
     \label{fig:papelstd}
@@
 
-In Fig. \ref{fig:papelilllevel} we present the relation between an average value of $\sigma_p$,
-in the $\sigma$ matrix, with a value $\mu_p$ (mean value representing the observable illumination level) of the $\mu$ matrix, 
+Fig.~\ref{fig:papelilllevel} presents the relation between the average value of $\sigma_p$,
+in the $\sigma$ matrix, with the value of $\mu_p$ (the mean value representing the observable level of illumination) of the $\mu$ matrix, 
 in the complete frequency band, the value $\mu_p$
-is related to the laser illumination level in the surface of the sample \cite{Nothdurft:05}
-and the color of it. Thus, when we choose $\mu_p$  as reference 
+is related to the level of the laser illumination of the surface of the sample \cite{Nothdurft:05}
+and its colour. Thus, when we choose $\mu_p$  as reference
 in a homogeneous sample,
-in true we choose indirectly the observable illumination level in the surface.
-Therefore, Fig. \ref{fig:papelilllevel} shows the variables $\sigma_p$, $e_p$ and $L_p$ in function
-of  $\mu_p$, to the case of the complete frequency band (\ref{fig:illlevel_all}), the inferior third of the frequency band (\ref{fig:illlevel_stdx}),
-the middle third of the frequency band (\ref{fig:illlevel_stdy}) and the superior third of the frequency band (\ref{fig:illlevel_stdz}).
-It is import to note that $e_p$ was plot as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$,
-and $L_p$ is the histogram of the values in temporal speckle mean matrix.
-Given that the mean value is zero to any frequency band without the zero frequency,
-in the figures are showed the $L_p$ values of the complete frequency band, 
-with the objective of to have a reference of the illumination level and the number of pixels involved in the analysis.
+we are choosing indirectly the observable level of illumination in the surface.
+Therefore, Fig.~\ref{fig:papelilllevel} shows the variables $\sigma_p$, $e_p$ and $L_p$ as functions
+of  $\mu_p$, for the case of the complete frequency band (\ref{fig:illlevel_all}), 
+the lower third of the frequency band (\ref{fig:illlevel_stdx}),
+the middle third of the frequency band (\ref{fig:illlevel_stdy}) 
+and the upper third of the frequency band (\ref{fig:illlevel_stdz}).
+It is important to note that $e_p$ was reinterpreted and plotted as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p}\%$,
+and $L_p$ is the histogram of the values in the temporal speckle mean matrix.
+Given that the mean value is zero for any frequency band without the zero frequency,
+the figures show the values of $L_p$ for the complete frequency band, 
+with the objective of having a reference for the level of illumination and the number of pixels involved in the analysis.
 
@@
         \includegraphics[width=\textwidth]{stdx_curve.eps}
-	\caption{Analysis in the inferior third of the frequency band.}
+	\caption{Analysis in the lower third of the frequency band.}
         \label{fig:illlevel_stdx}
@@
         \includegraphics[width=\textwidth]{stdz_curve.eps}
-	\caption{Analysis in the superior third of the frequency band.}
+	\caption{Analysis in the upper third of the frequency band.}
         \label{fig:illlevel_stdz}
@@
 
-    \caption{Relation between the standard deviation value and the illumination level in a steady paper under laser illumination.}
+    \caption{Relation between the standard deviation and the level of illumination for steady paper under laser illumination.}
     \label{fig:papelilllevel}
@@
 
-In Fig.
-\ref{fig:illlevel_all}, we observe the absence of tendency in the DLSI ($\sigma$) with respect to the intensity ($\mu$), i.e.
-with the increase of the $\mu$ value the standard deviation ($\sigma$) does not increase or decrease.
-However, around that constant there is a spread of $\sigma$ to each value of $\mu$ that creates an uncertainty in the outcome, and expressed by the error $e$. 
-Fig. \ref{fig:illlevel_all} represents the outcome from the data without filtering, thus with all frequencies. 
-And the data are the speckle signals present in a material with low activity, because the sample is a steady paper approximately homogeneous over time and space.
+In Fig.~\ref{fig:illlevel_all}, we can see the absence of a tendency in the DLSI ($\sigma$) 
+with respect to the intensity ($\mu$), 
+i.e. with an increase of $\mu$, the standard deviation ($\sigma$) neither increases nor decreases.
+However, around that constant there is a uncertainty of $\sigma$ for each value of $\mu$, which creates an uncertainty in the outcome, 
+and is expressed by the error $e$.
+Fig.~\ref{fig:illlevel_all} represents the outcome from the data without filtering, thus with all frequencies.
+The data are the speckle signals present in a material with low activity, 
+because the sample is a steady paper approximately homogeneous over time and space.
 Nevertheless, when we filter the signal (images in time), 
-we can observe a change in the $\sigma$ with respect to the frequency range, 
-unveiling the dependency of the DLSI to the level of illumination and its relation to the frequency.
-In Fig. \ref{fig:illlevel_stdx}, corresponding to the inferior third of the frequency band, 
-there is a tendency in the $\sigma$ value with respect to the level of light. 
-The DLSI changes its value with respect to the illumination level $\mu_p$, 
-where in low illumination level we had highest error, 
-%with the $\sigma$ values spread around the mean value, 
-and the error tending to zero when the level of light ($\mu_p$) increased in some areas of the sample. 
-The same behavior happened in the middle level of frequency band, 
-and much less in the superior third of the frequency band, 
-meaning that in the highest frequencies one had less influence of the level of light ($\mu_p$) in the $\sigma$ values. 
-Since the $\sigma$ DLSI does not filter the signal \cite{RIVERA2017144}, 
-it must be considered this situation during the usage of any DLSI, 
-and of how this one can compromise the outcome by the influence of the illumination of the sample in the results.
-Other dynamic laser speckle indexes may offer other options to avoid this influence,
+we observe a change in $\sigma$ with respect to the frequency range, 
+revealing the dependence of the DLSI on the level of illumination and its relation with the frequency.
+In Fig.~\ref{fig:illlevel_stdx}, corresponding to the lower third of the frequency band, 
+there is a tendency of $\sigma$ with respect to the level of illumination.
+The DLSI changes its value with  changes in the level of illumination $\mu_p$:
+at low levels of illumination we have the highest error, 
+but the error tends to zero when the level of illumination ($\mu_p$) increases in some areas of the sample.
+The same happens in the middle of the frequency band, 
+but much less in the upper third of the frequency band, 
+meaning that in the highest frequencies there is less influence of the level of illumination on $\sigma$.
+Since the 
+temporal speckle deviation index
+%$\sigma$ DLSI 
+does not filter the signal \cite{RIVERA2017144}, 
+this phenomenon must be taken into consideration during the use of this DLSI, 
+and how this can compromise the outcome by the influence of the illumination of the sample on the results.
+Other dynamic laser speckle indices may offer other options to avoid this influence,
 for example, using the Absolute Value of the Differences DLSI and its variations \cite{BSLTLBOOK}.
 
-\subsection{Fujii index in the ink drying test} 
+\subsection{The Fujii index in the ink drying test} 
 \label{subsec:vsfujii}
 
-The Fig. \ref{fig:fujiiallink} shows the behavior of mean value to the Fujii matrix
-defined in the Equation \ref{eq:contFujii2}.
-The Figs. \ref{fig:fujiixink}, \ref{fig:fujiiyink} and \ref{fig:fujiizink},
-show the behavior of mean value to the Fujii matrix defined in the Equation \ref{eq:contFujii3},
-to the cases of frequency bands X,Y and Z respectively. In all cases we worked on the ink drying test.
+Fig.~\ref{fig:fujiiallink} shows the behaviour of the mean value of the Fujii matrix
+defined in Eq.~\ref{eq:contFujii2}.
+Figs~\ref{fig:fujiixink}, \ref{fig:fujiiyink} and \ref{fig:fujiizink},
+show the behaviour of the mean value of the Fujii matrix defined in Eq.~\ref{eq:contFujii3},
+for the frequency bands X, Y and Z, respectively. All cases treat the ink drying test.
 \begin{figure}[!h]
@@
 
-\caption{Numerical results in the ink drying test using Fujii index.}
+\caption{Numerical results for the ink drying test using the Fujii index.}
 \label{fig:numericalvsfujii}
@@
 
-As can be seen in all the images, the curves with more and less  illumination level are close,
-but there is no advantage in separating the signals by bands
-this can be explained if we analyze how the index synthesizes its value and we compares it with the images.
-First the Fujii index makes a high pass filtering,
+As can be seen in all the images, the curves with greater or lesser  illumination levels are close,
+but there is no advantage in separating the signals by bands.
+This can be explained if we analyse how the index synthesizes its value and we compare it with the images.
+First, the Fujii index makes a high pass filtering:
 this is evident if we look at the maximum values of the curves,
-being greater in the Z (high frequencies) band and rapidly decrease in the Y and X (low frequencies) bands.
-Second, the index undergoes a normalization, in the denominator of the Equation \ref{eq:contFujii2},
-with the intention of reducing the index dependence with the sample level of illumination.
-Not to mention that this normalization, in the case of frequency band analysis, is done with unfiltered signal data.
+which are greater in the Z (high frequencies) band and rapidly decrease in the Y and X (low frequencies) bands.
+Second, the index undergoes a normalization, in the denominator of Eq.~\ref{eq:contFujii2},
+with the intention of reducing the dependence of the index on the level of illumination of the sample,
+not to mention that this normalization, in the case of a frequency band analysis, is done with the unfiltered signal data.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Final comments}
+
+Using the results shown in Figs~\ref{fig:numerical} and \ref{fig:papelilllevel},
+we can theorize that 
+the difference between index values, of a phenomenom to given time,
+%the dynamic range between the samples with greater and  lesser values, 
+in  the temporal speckle deviation index,
+are greater in speckle signals with low frequency components, 
+and  smaller in speckle signals with high frequency components;
+thus, we can observe that the effect of the level of illumination on 
+the variability of the temporal speckle deviation index decreases with the frequency.
+This hypothesis is supported by other publications with similar results \cite{Nothdurft:05},
+where the temporal speckle mean matrix shows information about the surface of the sample and the ``laser illumination level'', 
+and the temporal speckle deviation matrix shows information of the material inside at 
+different levels and ``in less proportion the information of the laser illumination level''.
+Given that the mean value collects information of the zero frequency component in the speckle signal, 
+and the standard deviation  collects information of the non-zero frequency components,
+we can make a parallel
+with the results obtained in the present paper,
+which indicates that, to a given time, the speckle signals with high frequency components
+ are less affected in their index values by the variation of the intensity of the laser illumination.
+By analysing the Fujii index, 
+we also stress that generalizations cannot be made for all speckle indices.
+In this paper we mainly used the standard deviation, because its calculation is directly linked to the value, 
+or amplitude, of the root mean square of the signals.
+In contrast, the Fujii index makes a previous filtering (subtract a sample from the previous one) 
+and a non-linear scaling with respect to the light intensity (divide by the average intensity of the two consecutive samples), 
+which hinders a fair interpretation of its behaviour for different frequency bands.
+
 \section{Conclusion}
@@
 In the ink drying test, 
-we analyzed the effect produced in  the speckle light intensity and, consequently, in the standard deviation index, 
-by the separation of the signals in different frequency bands;
-when there was a process that changes its behavior over time.
+we analysed a process that changes its behaviour over time,
+and have seen the effect produced on  the speckle light intensity, 
+and consequently on the standard deviation index, 
+produced by the separation of the signals into different frequency bands.
+On the other hand, in the test using a piece of paper, 
+we took into consideration the fact that no material is completely inert and, consequently, 
+the observed signal  in the  dynamic speckle analysis has more than just noise.
 
-In the paper piece test, we considered that none material is completely inert and, consequently, 
-the observed signal  in the  dynamic speckle analysis has more than noise.
+By the analysis of a piece of paper, as shown in Figs~\ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
+we can see that the greater the observable laser level of illumination $\mu_p$, 
+the greater will be the $\sigma_p$ index of each pixel analysed. 
+However, this increase depends on the frequency band in the speckle signal  analysed;
+for example, in Fig.~\ref{fig:illlevel_stdz},
+with high frequency components, the relation between $\mu_p$ and $\sigma_p$ is almost a horizontal line, 
+which means that a variation of $\mu_p$ does not affect significantly the $\sigma_p$ index.
+This is reaffirmed by the analysis of the ink drying test, 
+seen in Figs~\ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
+where the curves of regions with high and low luminosity are compared in different frequency bands:
+here, the high frequency band  (Fig.~\ref{fig:stdzink}) 
+is the one that produces very similar indices, despite the difference in the level of illumination.
 
-By the analysis shown in the Figs. \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
-we can observe that the greater the laser illumination level $\mu_p$, 
-the greater the range of speckle light intensity variation $\sigma_p$ of each pixel analyzed, 
-however this increase depend of speckle signal frequency band analyzed.
-This is reaffirmed by the analysis of the ink drying test, 
-seen in the Figs. \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
-where the curves of regions with high and low luminosity are compared.
-
-Thus, by the results shown in the Figs. \ref{fig:numerical} and \ref{fig:papelilllevel},
-we can theorize that this augmentative effect of the dynamic range in the speckle, acts predominantly on speckle signals with low frequency components, and in smaller predominance on speckle signals with high frequency components.
-This hypothesis is supported by other works with similar results \cite{Nothdurft:05},
-where the temporal speckle mean matrix shows information about the surface of sample and the laser illumination level, and the temporal speckle deviation matrix shows information of material inside at different levels and in less proportion the information of the laser illumination level.
-Given that the mean value collect information of zero frequency component in the speckle signal, 
-and the standard deviation  collect information of non-zero frequency components.
-We can make a parallel, with the results obtained in the present work,
-and thus  to indicate that the speckle signals with frequency components with greater value are less affected in their dynamic range by the variation of the laser light intensity.
-By analyzing the index Fujii, we also highlight that generalizations cannot be made for all speckle indices.
-In this work we mainly use the standard deviation, because its calculation is directly linked to the value, or amplitude, root mean square of the signals.
-In counter-parted, the Fujii index makes a previous filtering and a non-linear scaling with respect to the light intensity, which hinders a fair interpretation, of its behavior for different frequency bands.
-
-Thus, in this work were presented comparisons between the values of the temporal speckle deviation index for three different frequency bands of the speckle signal and different illuminations levels, 
-in a dynamic laser speckle analysis. 
-The results showed that the influence of the illumination level in a DLSI, 
+Thus, this paper compared the values of the temporal 
+speckle deviation index for three different frequency bands of the speckle signal and 
+different levels of illumination in a dynamic laser speckle analysis.
+The results showed that the influence of the observable level of illumination on the DLSI, 
 like the temporal speckle deviation index, 
@@
 \section{Acknowledgment}
-We wish to acknowledge the partial financial support for this study provided by the $CAPES$ 
+We wish to acknowledge the partial financial support for this study provided by the CAPES
 scholarship
-$PNPD$ Program, $FAPEMIG$ and $CNPQ$.
+PNPD Program, FAPEMIG and CNPQ.
 
-%----------------------------------------------------------------------------------------
-%	REFERENCE LIST
-%----------------------------------------------------------------------------------------
 \section{Bibliography}
-\bibliography{report}   %>>>> bibliography data in report.bib
-\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst
-
-%----------------------------------------------------------------------------------------
-
+\bibliography{report}
+\bibliographystyle{spiebib}
 \end{document}

### 2020-02-13 rev-ingles/Clean.sh

@@ -1,14 +1,0 @@
-#!/bin/bash
-
-rm -f *.aux
-rm -f *.dvi
-rm -f *.log  
-rm -f *.out
-rm -f *.blg
-rm -f *.bbl 
-rm -f *.spl
-rm -f *.backup 
-rm -f *.ps
-
-find . -type f -name "*.pdf" -not -name 'article_1.pdf'  -not -name 'Cover_Letter.pdf'| xargs rm
-

### 2020-02-13 article/article_1.tex
mejorando texto nivel de iluminacion

@@
 By the analysis of a piece of paper, as shown in Figs~\ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy} and \ref{fig:illlevel_stdz};
-we can see that the greater the observable laser level of illumination $\mu_p$, 
+we can see that the greater the observable laser illumination level $\mu_p$, 
 the greater will be the $\sigma_p$ index of each pixel analysed. 
